---
title: "Sign Language Interpreter Aptitude"
subtitle: "00 - Wrangling Set-up"
author: "anonymised for review"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    number_sections: false
    theme: flatly
    highlight: haddock
---

# Setup
```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

## Load packages
```{r load_packages, message = FALSE, warning = FALSE}
library(here) # file organisation & folder location
library(tidyverse) # data wrangling & plotting
library(naniar) # dealing with missing values
library(plotrix) # for calculating standard error
```

### R / package versions used
```{r r_package_versions, message = FALSE, warning = FALSE}
R.Version() 
packageVersion('here')
packageVersion('tidyverse')
packageVersion('psych')
```

## Read in data
```{r read_in_data}
#here::here()
apt <- read_csv(here("data", "apt-data.csv"))
apt <- as_tibble(apt)
```

# Look at data
```{r look_at_data}
head(apt)
tail(apt)
names(apt)
summary(apt)
```

## Overview of variables
*session* - testing session (1-4)
*group* - whether participants belonged to the first two cohorts or second two cohorts (first, second)     
*ppt* - randomized participant id codes to ensure anonymity (betwee   S01-S99)         
*selection* - whether participants were selected or rejected for the degree or not (selected, rejected)
*selected* -  as above in numeric form (1=selected, 0=rejected)
*continuation* - whether participants continued with the degree at the time of analysis (continuing, withdrew)
*continue* - as above in numeric form (1=continuing, 0=withdrew)    
*L1_bsl* - whether ppts were L1 signers of BSL or not (1=L1 BSL, 0=L2 BSL)    
*self_rating* - initial BSL self-rating on likert scale (1-7) at session 1 

*nback_lett* -  
*nback_spat* -  
*nback_comb* -  
*corsi_bspan* - 
*corsi_score* - 
*corsi_corr* -  
*corsi_mspan*
*kirk_ceil* -   
*kirk_raw* -    
*kirk_acc* -    
*kbit_ceil* -   
*kbit_raw* -    
*kbit_acc* -    
*dspan_mem* -   
*dspan_corr* - 
*dspan_time* -  
*mr2d_acc* -    
*mr2d_rt* -     
*mr2d_sats* -   
*mr3d_acc* -    
*mr3d_rt* -     
*mr3d_sats* -   
*bis_tot* -    
*bis_att* -     
*bis_mot* -     
*bis_nplan* -   
*mlat_raw* -    
*mlat_acc* -    
*summ* -        
*copy_sign* -   
*bsl_srt* -    
*town_map* -    
*terp_b2e* -    
*terp_e2b* -    
*grade_bsl* -   
*grade_terp* -  
*comments* - 


## Summarise missingness
```{r}
apt %>% select(-session:-ppt, -comments) %>% 
  naniar::miss_var_summary() # data is in long format though

apt_wide <- apt %>% 
  tidyr::pivot_wider(names_from = session, 
                     values_from = c(nback_lett:comments))

naniar::miss_var_summary(apt_wide)

vis_miss(apt) # visualise missingness
vis_miss(apt_wide) # visualise missingness
vis_miss(apt, cluster = TRUE) # arrange rows according to missingness

# Show missingness on a row by row basis i.e. by participant & session
gg_miss_case(apt)
```
Not all of the missingness is a problem, for some variables we did not plan to test on all participants

### Convert variables   

Fix the variables that are character when they should be factor, or numeric:  
```{r convert_variables}
# convert session, group, ppt & status to factor
apt <- mutate(apt, across(c("session", "group", "ppt", "selection", "continuation"), factor))

# convert these character variables to numeric
apt <- mutate(apt, across(c("L1_bsl", "age_s1", "self_rating", "dspan_time",
                            "bis_tot", "bis_att","bis_mot", "bis_nplan", "summ",
                            "copy_sign", "copy_sign", "bsl_srt", "town_map",
                            "terp_b2e"), as.numeric))
```


Calculate speed-accuracy trade off-scores for mental rotation data:
```{r speed-acc}
# Create speed accuracy trade-off score function (Balanced Integration Score; BIS)
# (Liesefeld, Fu, & Zimmer, 2015; Liesefeld & Janczyk, in press)

BIS <- function(data) {
  n <- length(data$group)   # sample size to correct var()-function result (which uses n-1)
  srt <- sqrt( ((n-1)/n) * var(data$mean_rt_c) )  # sample standard deviation across all rts
  spc <- sqrt( ((n-1)/n) * var(data$pc) ) # sample standard deviation across all rts
  mrt <- mean(data$mean_rt_c)                     # mean across all rts
  mpc <- mean(data$pc)                            # mean across all pcs
  zrt <- (data$mean_rt_c-mrt)/srt                 # standardized rts
  zpc <- (data$pc-mpc)/spc                        # z-standardized pcs
  data$bis <- zpc - zrt                           # Balanced Integration Score
  
  return(data)             # return data.frame with added variable 'bis'
}

# Extract relevant columns for 2D Mental Rotation data
mean_rt_c <- apt$mr2d_rt 
pc <- apt$mr2d_acc
group <- apt$session
ppt <- apt$ppt
data <- data.frame(group,ppt,mean_rt_c,pc)
data <- data %>% drop_na() # remove NAs

# create speed-accuracy trade off score (SATS, to avoid confusion with Baratt Impulsivity Scale), rename variables back to fit with original tibble
( SATS_mr2d <- BIS(data) %>% dplyr::rename(c(session = group, 
                                             mr2d_acc = pc,
                                             mr2d_rt = mean_rt_c,
                                             mr2d_sats = bis)) ) 

# join back to apt tibble
apt <- full_join(apt, SATS_mr2d) %>% relocate(mr2d_sats, .after = mr2d_rt )

# Same again for 3D Mental Rotation task
mean_rt_c <- apt$mr3d_rt 
pc <- apt$mr3d_acc
data <- data.frame(group,ppt,mean_rt_c,pc)
data <- data %>% drop_na() # remove NAs

# create SATS; rename variables back to fit with original tibble
( SATS_mr3d <- BIS(data) %>% dplyr::rename(c(session = group, 
                                             mr3d_acc = pc,
                                             mr3d_rt = mean_rt_c,
                                             mr3d_sats = bis)) ) 
# join back to apt tibble
apt <- full_join(apt, SATS_mr3d) %>% relocate(mr3d_sats, .after = mr3d_rt )
```

Rename levels of Session for tables/plotting:  
```{r relevel_session}
apt$session <- plyr::revalue(apt$session, c("1" = "pre-degree", 
                                            "2" = "1st year", 
                                            "3" = "2nd year",
                                            "4" = "3rd year"))
```

# Export data 
Export the wrangled data file for use in other analysis scripts as R data object:
```{r}
saveRDS(apt, here("data", "apt-data.rds"))
```