---
title: "Sign Language Interpreter Aptitude"
subtitle: "02 - Change over Time Analysis"
author:
  - name: "Freya Watkins"
    affiliation: "University of Birmingham"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    number_sections: false
    theme: flatly
    highlight: haddock
---

# Setup
```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

## Load packages
```{r load_packages, message = FALSE, warning = FALSE}
library(here) # file organisation & folder location
library(tidyverse) # data wrangling & plotting
library(PupillometryR) # raincloud plots
library(sdamr) # simultaneously nudge + jitter plot points
library(plotrix) # for calculating standard error
library(scales) # scales on plots
library(lme4) # for linear mixed models
library(afex) # for linear mixed models
library(psych) # for factor analysis
```

### R / package versions used
```{r r_package_versions, message = FALSE, warning = FALSE}
R.Version() 
packageVersion('here')
packageVersion('tidyverse')
packageVersion('PupillometryR')
packageVersion('sdamr')
packageVersion('plotrix') 
packageVersion('scales') 
packageVersion('lme4') 
packageVersion('afex')
packageVersion('psych')
```

## Read pre-wrangled data (see `00-wrangling-setup.Rmd` script)
```{r read_in_data}
here::here()
apt <- readRDS(here("data", "apt-data.rds"))
apt <- as_tibble(apt)
head(apt)
```

Filter out participants who did not progress beyond interview
```{r}
apt <- apt %>% filter(status != "rejected")
```

# Summary tables

## Cognitive & Linguistic predictors

### Dual N-Back
```{r nback_summary}
apt %>% 
  filter(!is.na(nback_lett)) %>% 
  group_by(session) %>% 
  summarise(nback_lett_mean = mean(nback_lett), 
            sd = sd(nback_lett),
            se = std.error(nback_lett))

apt %>% 
  filter(!is.na(nback_spat)) %>% 
  group_by(session) %>% 
  summarise(nback_spat_mean = mean(nback_spat), 
            sd = sd(nback_spat),
            se = std.error(nback_spat))

apt %>% 
  filter(!is.na(nback_comb)) %>% 
  group_by(session) %>% 
  summarise(nback_comb_mean = mean(nback_comb), 
            sd = sd(nback_comb),
            se = std.error(nback_comb))
```

### Corsi Blocks
```{r corsi_summary}
apt %>% 
  filter(!is.na(corsi_bspan)) %>% 
  group_by(session) %>% 
  summarise(corsi_bspan_mean = mean(corsi_bspan), 
            sd = sd(corsi_bspan),
            se = std.error(corsi_bspan))

apt %>% 
  filter(!is.na(corsi_score)) %>% 
  group_by(session) %>% 
  summarise(corsi_score_mean = mean(corsi_score), 
            sd = sd(corsi_score),
            se = std.error(corsi_score))

apt %>% 
  filter(!is.na(corsi_corr)) %>% 
  group_by(session) %>% 
  summarise(corsi_corr_mean = mean(corsi_corr), 
            sd = sd(corsi_corr),
            se = std.error(corsi_corr))

apt %>% 
  filter(!is.na(corsi_mspan)) %>% 
  group_by(session) %>% 
  summarise(corsi_mspan_mean = mean(corsi_mspan), 
            sd = sd(corsi_mspan),
            se = std.error(corsi_mspan))
```

### Kirklees Sentence Reading
```{r kirklees_summary}
apt %>% 
  filter(!is.na(kirk_ceil)) %>% 
  group_by(session) %>% 
  summarise(kirk_ceil_mean = mean(kirk_ceil), 
            sd = sd(kirk_ceil),
            se = std.error(kirk_ceil))

apt %>% 
  filter(!is.na(kirk_raw)) %>% 
  group_by(session) %>% 
  summarise(kirk_raw_mean = mean(kirk_raw), 
            sd = sd(kirk_raw),
            se = std.error(kirk_raw))

apt %>% 
  filter(!is.na(kirk_acc)) %>% 
  group_by(session) %>% 
  summarise(kirk_acc_mean = mean(kirk_acc), 
            sd = sd(kirk_acc),
            se = std.error(kirk_acc))
```

### KBIT-2 Matrices
```{r kbit_summary}
apt %>% 
  filter(!is.na(kbit_ceil)) %>% 
  group_by(session) %>% 
  summarise(kirk_ceil_mean = mean(kbit_ceil), 
            sd = sd(kbit_ceil),
            se = std.error(kbit_ceil))

apt %>% 
  filter(!is.na(kbit_raw)) %>% 
  group_by(session) %>% 
  summarise(kbit_raw_mean = mean(kbit_raw), 
            sd = sd(kbit_raw),
            se = std.error(kbit_raw))

apt %>% 
  filter(!is.na(kbit_acc)) %>% 
  group_by(session) %>% 
  summarise(kbit_acc_mean = mean(kbit_acc), 
            sd = sd(kbit_acc),
            se = std.error(kbit_acc))
```

### Digit Span
```{r dspan_summary}
apt %>% 
  filter(!is.na(dspan_mem)) %>% 
  group_by(session) %>% 
  summarise(dspan_mem_mean = mean(dspan_mem), 
            sd = sd(dspan_mem),
            se = std.error(dspan_mem))

apt %>% 
  filter(!is.na(dspan_corr)) %>% 
  group_by(session) %>% 
  summarise(dspan_corr_mean = mean(dspan_corr), 
            sd = sd(dspan_corr),
            se = std.error(dspan_corr))
```

### 2D Mental Rotation
```{r 2dmr_summary}
apt %>% 
  filter(!is.na(mr2d_acc)) %>% 
  group_by(session) %>% 
  summarise(mr2d_acc_mean = mean(mr2d_acc), 
            sd = sd(mr2d_acc),
            se = std.error(mr2d_acc))

apt %>% 
  filter(!is.na(mr2d_rt)) %>% 
  group_by(session) %>% 
  summarise(mr2d_rt_mean = mean(mr2d_rt), 
            sd = sd(mr2d_rt),
            se = std.error(mr2d_rt))

apt %>% 
  filter(!is.na(mr2d_sats)) %>% 
  group_by(session) %>% 
  summarise(mr2d_sats_mean = mean(mr2d_sats), 
            sd = sd(mr2d_sats),
            se = std.error(mr2d_sats))
```

### 3D Mental Rotation
```{r 3dmr_summary}
apt %>% 
  filter(!is.na(mr3d_acc)) %>% 
  group_by(session) %>% 
  summarise(mr3d_acc_mean = mean(mr3d_acc), 
            sd = sd(mr3d_acc),
            se = std.error(mr3d_acc))

apt %>% 
  filter(!is.na(mr3d_rt)) %>% 
  group_by(session) %>% 
  summarise(mr3d_rt_mean = mean(mr3d_rt), 
            sd = sd(mr3d_rt),
            se = std.error(mr3d_rt))

apt %>% 
  filter(!is.na(mr3d_sats)) %>% 
  group_by(session) %>% 
  summarise(mr3d_sats_mean = mean(mr3d_sats), 
            sd = sd(mr3d_sats),
            se = std.error(mr3d_sats))
```

### Barratt Impulsivity Scale
```{r bis_summary}
apt %>% 
  filter(!is.na(bis_tot)) %>% 
  group_by(session) %>% 
  summarise(bis_tot_mean = mean(bis_tot), 
            sd = sd(bis_tot),
            se = std.error(bis_tot))

apt %>% 
  filter(!is.na(bis_att)) %>% 
  group_by(session) %>% 
  summarise(bis_att_mean = mean(bis_att), 
            sd = sd(bis_att),
            se = std.error(bis_att))

apt %>% 
  filter(!is.na(bis_mot)) %>% 
  group_by(session) %>% 
  summarise(bis_mot_mean = mean(bis_mot), 
            sd = sd(bis_mot),
            se = std.error(bis_mot))

apt %>% 
  filter(!is.na(bis_nplan)) %>% 
  group_by(session) %>% 
  summarise(bis_nplan_mean = mean(bis_nplan), 
            sd = sd(bis_nplan),
            se = std.error(bis_nplan))
```

### MLAT Number Learning
Only collected at session 1, grant cohort only

### Summarising Task
Only collected at session 1, grant cohort only

## BSL / Interpreting outcome variables

### Copy Sign Task
```{r copy_sign}
# data to be coded
```

### BSL Sentence Reproduction Task
```{r bslsrt}
apt %>% 
  filter(!is.na(bsl_srt)) %>% 
  group_by(session) %>% 
  summarise(grade_bsl_mean = mean(bsl_srt), 
            sd = sd(bsl_srt),
            se = std.error(bsl_srt))

# still some data to be coded/checked
```

### BSL Town Map
```{r town_map}
# data to be coded
```

### BSL Grades
```{r grades_bsl}
apt %>% 
  filter(!is.na(grade_bsl)) %>% 
  group_by(session) %>% 
  summarise(grade_bsl_mean = mean(grade_bsl), 
            sd = sd(grade_bsl),
            se = std.error(grade_bsl))
```

### Interpreting Grades
```{r grades_terp}
apt %>% 
  filter(!is.na(grade_terp)) %>% 
  group_by(session) %>% 
  summarise(grade_terp_mean = mean(grade_terp), 
            sd = sd(grade_terp),
            se = std.error(grade_terp))
```

## Plots

Let's plot the linguistic & cognitive assessments over time 

```{r plot-theme}
# set up a theme for the plots
theme_details <- theme_bw() + 
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          panel.border = element_rect(colour = "black", size=0.5),
          plot.title = element_text(face = "bold"),
          axis.title.x = element_text(face = "bold"),
          axis.title.y = element_text(face = "bold"),
          axis.text.x = element_text(size=10, colour="black"),
          axis.text.y = element_text(colour="black"),
          legend.position = "none")
```

### Dual N-Back
#### Accuracy in letter matching
```{r nback_lett}
# Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(nback_lett)) %>% 
  ggplot(aes(x = session, y = nback_lett, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
 #geom_boxplot(position = position_nudge(x = .2, y = 0),
 #                width = .2, alpha = 1) +
  geom_point(position = position_jitter(width = .15), 
                        size = 0.5) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +  
  scale_y_continuous(labels = percent_format(accuracy=1)) +
  labs(title = "Accuracy in letter matching during Dual N-Back Task by Session", 
       x = "Session", y = "Accuracy") +
  theme_details )
  
# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(nback_lett)) %>% 
  summarize(mean=mean(nback_lett), sd = sd(nback_lett), se=std.error(nback_lett)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  coord_cartesian(ylim = c(0.5, 0.8)) +
  theme_minimal() +
  scale_y_continuous(labels = percent_format(accuracy=1)) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  labs(title = "Accuracy in letter matching during Dual N-Back Task by Session", 
       x = "Session", y = "Accuracy")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5) +
  scale_y_continuous(labels = percent_format(accuracy=1)) 

indiv <- apt %>% 
  filter(!is.na(nback_lett)) %>% 
  group_by(session, ppt) %>% 
  summarise(mean = mean(nback_lett)) #, sd = sd(nback_lett)) # requires trial level data

pd <- position_dodge(0.5)
J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details )
```

#### Accuracy in spatial matching
```{r nback_spat}
# Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(nback_spat)) %>% 
  ggplot(aes(x = session, y = nback_spat, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitter(width = .15), 
                        size = 0.5) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +  
  scale_y_continuous(labels = scales::percent_format(accuracy = 1L)) +
  labs(title = "Accuracy in spatial matching during Dual N-Back Task by Session", 
       x = "Session", y = "Accuracy") +
  theme_details )
  
# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(nback_spat)) %>% 
  summarize(mean=mean(nback_spat), sd = sd(nback_spat), se=std.error(nback_spat)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  coord_cartesian(ylim = c(0.5, 0.8)) +
  theme_minimal() +
  scale_y_continuous(labels = percent_format(accuracy=1)) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  labs(title = "Accuracy in spatial matching during Dual N-Back Task by Session", 
       x = "Session", y = "Accuracy")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5) +
  scale_y_continuous(labels = percent_format(accuracy=1)) 

indiv <- apt %>% 
  filter(!is.na(nback_spat)) %>% 
  group_by(session, ppt) %>% 
  summarise(mean = mean(nback_spat)) #, sd = sd(nback_spat)) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details )
```

#### Combined accuracy
```{r nback_comb}
## Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(nback_comb)) %>% 
  ggplot(aes(x = session, y = nback_comb, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitternudge(jitter.width = .4, nudge.x = -.15), 
                        size = 2, shape = 21) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +  
  scale_y_continuous(labels = percent_format(accuracy=1)) +
  labs(title = "Combined accuracy on Dual N-Back Task by Session", 
       x = "Session", y = "Accuracy") +
  theme_details )

# Jitter plot  
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(nback_comb)) %>% 
  summarize(mean=mean(nback_comb), sd = sd(nback_comb), se=std.error(nback_comb)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  coord_cartesian(ylim = c(0.5, 0.8)) +
  theme_minimal() +
  scale_y_continuous(labels = percent_format(accuracy=1)) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  labs(title = "Combined accuracy on Dual N-Back Task by Session", 
       x = "Session", y = "Accuracy")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5) +
  scale_y_continuous(labels = percent_format(accuracy=1))

indiv <- apt %>% 
  filter(!is.na(nback_comb)) %>% 
  group_by(session, ppt) %>% 
  summarise(mean = mean(nback_comb)) #, sd = sd(nback_comb)) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details ) 
```

### Corsi Blocks
#### Block Span
```{r corsi_bspan}
# Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(corsi_bspan)) %>% 
  ggplot(aes(x = session, y = corsi_bspan, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitternudge(jitter.width = .4,
                                             nudge.x = -.15), 
                        size = 2, shape = 21) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +    
  labs(title = "Block span on Corsi Blocks Task by Session", 
       x = "Session", y = "Block Span") +
  theme_details )

# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(corsi_bspan)) %>% 
  summarize(mean=mean(corsi_bspan), sd = sd(corsi_bspan), se=std.error(corsi_bspan)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(0, 10)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  labs(title = "Block span on Corsi Blocks Task by Session", 
       x = "Session", y = "Block Span")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  filter(!is.na(corsi_bspan)) %>% 
  group_by(session, ppt) %>% 
  summarise(mean = mean(corsi_bspan)) #, sd = sd(corsi_bspan)) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details ) 
```

#### Raw Score
```{r corsi_score}
# Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(corsi_score)) %>% 
  ggplot(aes(x = session, y = corsi_score, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitternudge(jitter.width = .4, nudge.x = -.15), 
                        size = 2, shape = 21) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +  
  labs(title = "Raw Score on Corsi Blocks Task by Session", 
       x = "Session", y = "Score") +
  theme_details)
  
# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(corsi_score)) %>% 
  summarize(mean=mean(corsi_score), 
            sd = sd(corsi_score), se=std.error(corsi_score)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(0, 125)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  labs(title = "Raw Score on Corsi Blocks Task by Session", 
       x = "Session", y = "Score")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  filter(!is.na(corsi_score)) %>% 
  group_by(session, ppt) %>% 
  summarise(mean = mean(corsi_score)) #, sd = sd(corsi_score)) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details )
```

#### Correct Responses
```{r corsi_corr}
# Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(corsi_corr)) %>% 
  ggplot(aes(x = session, y = corsi_corr, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitternudge(jitter.width = .4, nudge.x = -.15), 
                        size = 2, shape = 21) +
  coord_cartesian(ylim = c(5, 15)) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +  
  scale_y_continuous(labels = scales::number_format(accuracy = 1)) +
  labs(title = "Correct Responses on Corsi Blocks Task by Session", 
       x = "Session", y = "Correct Response") +
  theme_details )

# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(corsi_corr)) %>% 
  summarize(mean=mean(corsi_corr), sd = sd(corsi_corr), se=std.error(corsi_corr)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(0, 15)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  labs(title = "Correct Responses on Corsi Blocks Task by Session", 
       x = "Session", y = "Correct Response")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  filter(!is.na(corsi_corr)) %>% 
  group_by(session, ppt) %>% 
  summarise(mean = mean(corsi_corr)) #, sd = sd(corsi_corr)) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details ) 
```

#### Memory Span
```{r corsi_mspan}
# Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(corsi_mspan)) %>% 
  ggplot(aes(x = session, y = corsi_mspan, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitter(width = .15), 
                        size = 0.5) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +    
  labs(title = "Memory Span on Corsi Blocks Task by Session", 
       x = "Session", y = "Memory Span") +
  theme_details )
  
# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(corsi_mspan)) %>% 
  summarize(mean=mean(corsi_mspan), sd = sd(corsi_mspan), se=std.error(corsi_mspan)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(0, 8)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  labs(title = "Memory Span on Corsi Blocks Task by Session", 
       x = "Session", y = "Memory Span")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  filter(!is.na(corsi_mspan)) %>% 
  group_by(session, ppt) %>% 
  summarise(mean = mean(corsi_mspan)) #, sd = sd(corsi_mspan)) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details )
```

### Kirklees Sentence Reading
#### Ceiling Score
```{r kirk_ceil}
# Raincloud plot
( R1 <- apt %>% 
  #filter(!is.na(kirk_ceil)) %>% 
  ggplot(aes(x = session, y = kirk_ceil, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitter(width = .15), 
                        size = 0.5) +
  scale_fill_manual(values = c("#7bccc4", "#43a2ca", "#0868ac", "#bae4bc")) +    
  labs(title = "Ceiling Score on Kirklees Sentence Reading Task by Session", 
       x = "Session", y = "Ceiling Score") +
  theme_details )
  
# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  #filter(!is.na(kirk_ceil)) %>% 
  summarize(mean=mean(kirk_ceil), sd = sd(kirk_ceil), se=std.error(kirk_ceil)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(0, 45)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  labs(title = "Ceiling Score on Kirklees Sentence Reading Task by Session", 
       x = "Session", y = "Ceiling Score")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  #filter(!is.na(kirk_ceil)) %>% 
  group_by(session, ppt) %>% 
  summarise(mean = mean(kirk_ceil)) #, sd = sd(kirk_ceil) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details )
```

#### Raw Score
```{r kirk_raw}
# Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(kirk_raw)) %>% 
  ggplot(aes(x = session, y = kirk_raw, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitter(width = .15), 
                        size = 0.5) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +  
  labs(title = "Raw Score on Kirklees Sentence Reading Task by Session", 
       x = "Session", y = "Raw Score") +
  theme_details )
  
# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(kirk_raw)) %>% 
  summarize(mean=mean(kirk_raw), sd = sd(kirk_raw), se=std.error(kirk_raw)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(0, 45)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  labs(title = "Raw Score on Kirklees Sentence Reading Task by Session", 
       x = "Session", y = "Raw Score")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  filter(!is.na(kirk_raw)) %>% 
  group_by(session, ppt) %>% 
  summarise(mean = mean(kirk_raw)) #, sd = sd(kirk_raw) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details )
```

#### Accuracy
```{r kirk_acc}
# Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(kirk_acc)) %>% 
  ggplot(aes(x = session, y = kirk_acc, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitter(width = .15), 
                        size = 0.5) +
  coord_cartesian(ylim = c(0.45, 1)) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +  
  scale_y_continuous(labels = percent_format(accuracy=1)) +
  labs(title = "Accuracy on Kirklees Sentence Reading Task by Session", 
       x = "Session", y = "Accuracy") +
  theme_details )
  
# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(kirk_acc)) %>% 
  summarize(mean=mean(kirk_acc), sd = sd(kirk_acc), se=std.error(kirk_acc)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(0, 1)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  scale_y_continuous(labels = percent_format(accuracy=1)) +
  labs(title = "Accuracy on Kirklees Sentence Reading Task by Session", 
       x = "Session", y = "Accuracy")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  filter(!is.na(kirk_acc)) %>% 
  group_by(session, ppt) %>% 
  summarise(mean = mean(kirk_acc)) #, sd = sd(kirk_acc) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details ) 
```

### KBIT-2 Matrices

#### Ceiling Score
```{r kbit_ceil}
# Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(kbit_ceil)) %>% 
  ggplot(aes(x = session, y = kbit_ceil, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitter(width = .15), 
                        size = 0.5) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +  
  labs(title = "Ceiling Score on KBIT-2 Matrices Task by Session", 
       x = "Session", y = "Ceiling Score") )
  
# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(kbit_ceil)) %>% 
  summarize(mean=mean(kbit_ceil), sd = sd(kbit_ceil), se=std.error(kbit_ceil)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(0, 48)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  labs(title = "Ceiling Score on KBIT-2 Matrices Task by Session", 
       x = "Session", y = "Ceiling Score")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  filter(!is.na(kirk_ceil)) %>% 
  group_by(session, ppt) %>% 
  summarise(mean = mean(kbit_ceil)) #, sd = sd(kbit_ceil) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details )
```

#### Raw Score
```{r kbit_raw}
# Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(kbit_raw)) %>% 
  ggplot(aes(x = session, y = kbit_raw, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitter(width = .15), 
                        size = 0.5) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +  
  labs(title = "Raw Score on KBIT-2 Matrices Task by Session", 
       x = "Session", y = "Ceiling Score") )
  
# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(kbit_raw)) %>% 
  summarize(mean=mean(kbit_raw), sd = sd(kbit_raw), se=std.error(kbit_raw)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(0, 45)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca")) +
  labs(title = "Raw Score on KBIT-2 Matrices Task by Session", 
       x = "Session", y = "Raw Score")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  filter(!is.na(kbit_raw)) %>% 
  group_by(session, ppt) %>% 
  summarise(mean = mean(kbit_raw)) #, sd = sd(kbit_raw) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details ) 
```

#### Accuracy
```{r kbit_acc}
# Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(kbit_acc)) %>% 
  ggplot(aes(x = session, y = kbit_acc, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitter(width = .15), 
                        size = 0.5) +
  coord_cartesian(ylim = c(.65, 1)) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +  
  scale_y_continuous(labels = percent_format(accuracy=1)) +
  labs(title = "Accuracy on KBIT-2 Matrices Task by Session", 
       x = "Session", y = "Accuracy") )
  
# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(kbit_acc)) %>% 
  summarize(mean=mean(kbit_acc), 
            sd = sd(kbit_acc), se=std.error(kbit_acc)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(.5, 1)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  scale_y_continuous(labels = percent_format(accuracy=1)) +
  labs(title = "Accuracy on KBIT-2 Matrices Task by Session", 
       x = "Session", y = "Accuracy")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  filter(!is.na(kbit_acc)) %>% 
  group_by(session, ppt) %>% 
  summarise(mean = mean(kbit_acc)) #, sd = sd(kbit_acc) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details )  
```

### Digit Span
#### Accuracy
```{r dspan_corr}
# Raincloud plot
( R1 <- apt %>% 
  #filter(!is.na(dspan_corr)) %>% 
  ggplot(aes(x = session, y = dspan_corr, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitternudge(jitter.width = .4, nudge.x = -.15), 
                        size = 2, shape = 21) +
  coord_cartesian(ylim = c(0.5, 0.9)) +
  scale_fill_manual(values = c("#7bccc4", "#43a2ca", "#0868ac", "#bae4bc")) +  
  scale_y_continuous(labels = scales::percent_format(accuracy = 1L)) +
  labs(title = "Accuracy on Digit Span Task by Session", 
       x = "Session", y = "Accuracy") +
  theme_details )

# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  #filter(!is.na(dspan_corr)) %>% 
  summarize(mean=mean(dspan_corr), 
            sd = sd(dspan_corr), se=std.error(dspan_corr)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(0.5, 0.9)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1L)) +
  labs(title = "Accuracy on Digit Span Task by Session", 
       x = "Session", y = "Accuracy")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  #filter(!is.na(dspan_corr)) %>% 
  group_by(session, ppt) %>% 
  summarise(mean = mean(dspan_corr)) #, sd = sd(dspan_corr)) # requires trial-level data

indiv2 <- apt %>% 
  filter(!is.na(dspan_corr)) %>% 
  group_by(session, ppt) %>% 
  summarise(mean = mean(dspan_corr)) #, sd = sd(dspan_corr)) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv2, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details )
```

#### Memory Span
```{r dspan_mem}
# Raincloud plot
( R1 <- apt %>% 
  #filter(!is.na(dspan_mem)) %>% 
  ggplot(aes(x = session, y = dspan_mem, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitter(width = .15), 
                        size = 0.5) +
  coord_cartesian(ylim = c(4, 11)) +
  scale_fill_manual(values = c("#7bccc4", "#43a2ca", "#0868ac", "#bae4bc")) +   
  labs(title = "Memory Span on Digit Span Task by Session", 
       x = "Session", y = "Memory Span") +
  theme_details )
  
# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(dspan_mem)) %>% 
  summarize(mean=mean(dspan_mem), 
            sd = sd(dspan_mem), se=std.error(dspan_mem)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(0, 8)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#bae4bc", "#43a2ca", "#0868ac")) +
  coord_cartesian(ylim = c(4, 11)) +
  labs(title = "Memory Span on Digit Span Task by Session", 
       x = "Session", y = "Memory Span")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  filter(!is.na(dspan_mem)) %>% 
  group_by(session, ppt) %>% 
  summarise(mean = mean(dspan_mem)) #, sd = sd(dspan_mem)) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details )
```


### 2D Mental Rotation
#### Accuracy
```{r mr2d_acc}
# Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(mr2d_acc)) %>% 
  ggplot(aes(x = session, y = mr2d_acc, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitternudge(jitter.width = .4, nudge.x = -.15), 
                        size = 2, shape = 21) +
  coord_cartesian(ylim = c(0.5, 1)) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1L)) +
  labs(title = "Accuracy on 2D Mental Rotation Task by Session", 
       x = "Session", y = "Accuracy") +
  theme_details )

# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(mr2d_acc)) %>% 
  summarize(mean=mean(mr2d_acc), sd = sd(mr2d_acc), se=std.error(mr2d_acc)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(0.5, 1)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1L)) +
  labs(title = "Accuracy on 2D Mental Rotation Task by Session", 
       x = "Session", y = "Accuracy")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  filter(!is.na(mr2d_acc)) %>% 
  group_by(session, ppt) %>% 
  summarise(mean = mean(mr2d_acc)) #, sd = sd(mr2d_acc)) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details ) 

# Raincloud + Jitter
( RJ <- apt %>% 
  filter(!is.na(mr2d_acc)) %>% 
  ggplot(aes(x = session, y = mr2d_acc, group = session, fill = session)) +
  geom_point(data=indiv, aes(x = session, y = mean, group = ppt),
             position = position_jitternudge(jitter.width = .4, nudge.x = -.15), 
                        size = 2, shape = 21) +
  geom_line(data = indiv, aes(x = session, y = mean, group = ppt),
                      size = 0.1, alpha = 0.3, 
            position = position_jitternudge(jitter.width = .4, nudge.x = -.15)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  coord_cartesian(ylim = c(0.5, 1)) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1L)) +
  labs(title = "Accuracy on 2D Mental Rotation Task by Session", 
       x = "Session", y = "Accuracy") +
  theme_details )

```

#### Reaction Time
```{r mr2d_rt}
# Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(mr2d_rt)) %>% 
  ggplot(aes(x = session, y = mr2d_rt, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitter(width = .15), 
                        size = 0.5)  +
  coord_cartesian(ylim = c(0, 8500)) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  labs(title = "Reaction Time on 2D Mental Rotation Task by Session", 
       x = "Session", y = "RT (ms)") )

# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(mr2d_rt)) %>% 
  summarize(mean=mean(mr2d_rt), sd = sd(mr2d_rt), se=std.error(mr2d_rt)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(0, 8500)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  labs(title = "Reaction Time on 2D Mental Rotation Task by Session", 
       x = "Session", y = "RT (ms)")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  filter(!is.na(mr2d_rt)) %>% 
  filter(ppt != "HW025") %>% ## removing extreme outlier
  group_by(session, ppt) %>% 
  summarise(mean = mean(mr2d_rt)) #, sd = sd(mr2d_rt)) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details )


# Raincloud + Jitter plot
( RJ <- apt %>% 
  filter(!is.na(mr2d_rt)) %>% 
  filter(ppt != "HW025") %>% ## removing extreme outlier
  ggplot(aes(x = session, y = mr2d_rt, group = session, fill = session)) +
  geom_line(data = indiv, aes(x = session, y = mean, group = ppt),
                      size = 0.1, alpha = 0.3, position = pd) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(data=indiv, aes(x = session, y = mean, group = ppt), size = 2, 
                       shape = 21, position = pd) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  coord_cartesian(ylim = c(0, 4500)) +
  labs(title = "Reaction Time on 2D Mental Rotation Task by Session", 
       x = "Session", y = "RT (ms)") +
  theme_details )
```


#### Speed-Accuracy Trade-off Score
```{r mr2d-sats}
# Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(mr2d_sats)) %>% 
  ggplot(aes(x = session, y = mr2d_sats, group = session, fill = session)) +
  geom_hline(yintercept = 0, alpha = .3) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitter(width = .15), 
                        size = 0.5)  +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  coord_cartesian(ylim = c(-3, 3)) +
  labs(title = "Speed-Accuracy Trade-off Score on 2D Mental Rotation Task by Session", 
       x = "Session", 
       y = "Speed-Accuracy Trade-off Score\n(Balanced Integration Score") )

# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(mr2d_sats)) %>% 
  summarize(mean=mean(mr2d_sats), sd = sd(mr2d_sats), se=std.error(mr2d_sats)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(-3, 3)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  labs(title = "Speed-Accuracy Trade-off Score on 2D Mental Rotation Task by Session", 
       x = "Session", 
       y = "Speed-Accuracy Trade-off Score\n(Balanced Integration Score)")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  filter(!is.na(mr2d_sats)) %>% 
  group_by(session, ppt) %>% 
  summarise(mean = mean(mr2d_sats)) #, sd = sd(mr2d_rt)) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details )

( RJ <- apt %>% 
  filter(!is.na(mr2d_sats)) %>% 
  ggplot(aes(x = session, y = mr2d_sats, group = session, fill = session)) +
  geom_hline(yintercept = 0, alpha = 0.4, linetype = "dashed") +
  geom_line(data = indiv, aes(x = session, y = mean, group = ppt),
                      size = 0.1, alpha = 0.5, position = pd) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(data=indiv, aes(x = session, y = mean, group = ppt, fill = session),
             size = 2, shape = 21, position = pd) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  coord_cartesian(ylim = c(-3, 2)) +
  labs(title = "Speed-Accuracy Trade-off Score on 2D Mental Rotation Task by Session", 
       x = "Session", 
       y = "Speed-Accuracy Trade-off Score\n(Balanced Integration Score)") +
  theme_details )
```

### 3D Mental Rotation
#### Accuracy
```{r mr3d_acc}
# Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(mr3d_acc)) %>% 
  #filter(session != "1st year") %>% #only 2 ppts at 2nd session>filter out
  ggplot(aes(x = session, y = mr3d_acc, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitter(width = .15), 
                        size = 0.5)  +
  coord_cartesian(ylim = c(0, 1)) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1L)) +
  labs(title = "Accuracy on 3D Mental Rotation Task by Session", 
       x = "Session", y = "Accuracy") )

# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(mr3d_acc)) %>% 
  #filter(session != "1st year") %>% #only 2 ppts at 2nd session>filter out
  summarize(mean=mean(mr3d_acc), sd = sd(mr3d_acc), se=std.error(mr3d_acc)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(0, 1)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1L)) +
  labs(title = "Accuracy on 3D Mental Rotation Task by Session", 
       x = "Session", y = "Accuracy")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  filter(!is.na(mr3d_acc)) %>% 
  filter(session != "1st year") %>% #only 2 ppts at 2nd session>filter out
  group_by(session, ppt) %>% 
  summarise(mean = mean(mr3d_acc)) #, sd = sd(mr3d_acc)) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details ) 
```

#### Reaction Time
```{r mr3d_rt}
# Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(mr3d_rt)) %>% 
  filter(session != "1st year") %>% #only 2 ppts at 2nd session>filter out
  ggplot(aes(x = session, y = mr3d_rt, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitter(width = .15), 
                        size = 0.5)  +
  coord_cartesian(ylim = c(0, 4500)) +
  scale_fill_manual(values = c("#bae4bc", "#43a2ca", "#0868ac")) +
  labs(title = "Reaction Time on 3D Mental Rotation Task by Session", 
       x = "Session", y = "RT (ms)") )

# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(mr3d_rt)) %>% 
  filter(session != "1st year") %>% #only 2 ppts at 2nd session>filter out
  summarize(mean=mean(mr3d_rt), sd = sd(mr3d_rt), se=std.error(mr3d_rt)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(0, 4500)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#bae4bc", "#43a2ca", "#0868ac")) +
  labs(title = "Reaction Time on 3D Mental Rotation Task by Session", 
       x = "Session", y = "RT (ms)")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  filter(!is.na(mr3d_rt)) %>% 
  filter(session != "1st year") %>% #only 2 ppts at 2nd session>filter out
  group_by(session, ppt) %>% 
  summarise(mean = mean(mr3d_rt)) #, sd = sd(mr3d_rt)) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details )

# Raincloud + Jitter
( RJ <- apt %>% 
  filter(!is.na(mr3d_rt)) %>% 
  filter(session != "1st year") %>% #only 2 ppts at 2nd session>filter out
  ggplot(aes(x = session, y = mr3d_rt, group = session, fill = session)) +
  geom_line(data = indiv, aes(x = session, y = mean, group = ppt),
                      size = 0.1, alpha = 0.3, position = pd) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(data=indiv, aes(x = session, y = mean, group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
  scale_fill_manual(values = c("#bae4bc", "#43a2ca", "#0868ac")) +
  coord_cartesian(ylim = c(0, 4500)) +
  labs(title = "Reaction Time on 3D Mental Rotation Task by Session", 
       x = "Session", y = "RT (ms)") )
```

#### Speed-Accuracy Trade-off Score
```{r mr3d-sats}
# Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(mr3d_sats)) %>% 
  ggplot(aes(x = session, y = mr3d_sats, group = session, fill = session)) +
  geom_hline(yintercept = 0, alpha = .3) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitter(width = .15), 
                        size = 0.5)  +
  coord_cartesian(ylim = c(-4, 3)) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  labs(title = "Speed-Accuracy Trade-off Score on 3D Mental Rotation Task by Session", 
       x = "Session", 
       y = "Speed-Accuracy Trade-off Score\n(Balanced Integration Score)") )

# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(mr3d_sats)) %>% 
  #filter(session != "1st year") %>% #only 2 ppts at 2nd session>filter out
  summarize(mean=mean(mr3d_sats), sd = sd(mr3d_sats), se=std.error(mr3d_sats)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(-4, 3)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  labs(title = "Speed-Accuracy Trade-off Score on 3D Mental Rotation Task by Session", 
       x = "Session", 
       y = "Speed-Accuracy Trade-off Score\n(Balanced Integration Score)") 

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  filter(!is.na(mr3d_sats)) %>% 
  #filter(session != "1st year") %>% #only 2 ppts at 2nd session>filter out
  group_by(session, ppt) %>% 
  summarise(mean = mean(mr3d_sats)) #, sd = sd(mr3d_sats)) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details )

# Raincloud + Jitter

( RJ <- apt %>% 
  filter(!is.na(mr3d_sats)) %>% 
  ggplot(aes(x = session, y = mr3d_sats, group = session, fill = session)) +
  geom_hline(yintercept = 0, alpha = 0.4, linetype = "dashed") +
  geom_line(data = indiv, aes(x = session, y = mean, group = ppt),
                      size = 0.1, alpha = 0.5, position = pd) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(data=indiv, aes(x = session, y = mean, group = ppt, fill = session),
             size = 2, shape = 21, position = pd) +
  scale_fill_manual(values = c("#bae4bc", "#7bccc4", "#43a2ca", "#0868ac")) +
  coord_cartesian(ylim = c(-4, 3)) +
  labs(title = "Speed-Accuracy Trade-off Score on 3D Mental Rotation Task by Session", 
       x = "Session", 
       y = "Speed-Accuracy Trade-off Score\n(Balanced Integration Score)") +
  theme_details )
```

### Barratt Impulsivity Scale
#### Total Score
```{r bis_tot}
# Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(bis_tot)) %>% 
  filter(session != "1st year") %>% #only 2 ppts at 2nd session>filter out
  ggplot(aes(x = session, y = bis_tot, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitter(width = .15), 
                        size = 0.5)  +
  scale_fill_manual(values = c("#43a2ca", "#0868ac")) +
  coord_cartesian(ylim = c(0, 100)) +
  labs(title = "Total Score on Barratt Impulsivity Scale by Session", 
       x = "Session", y = "Total Score") )

# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(bis_tot)) %>% 
  filter(session != "1st year") %>% #only 2 ppts at 2nd session>filter out
  summarize(mean=mean(bis_tot), sd = sd(bis_tot), se=std.error(bis_tot)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(0, 100)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#43a2ca", "#0868ac")) +
  labs(title = "Total Score on Barratt Impulsivity Scale by Session", 
       x = "Session", y = "Total Score")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  filter(!is.na(bis_tot)) %>% 
  filter(session != "1st year") %>% #only 2 ppts at 2nd session>filter out
  group_by(session, ppt) %>% 
  summarise(mean = mean(bis_tot)) #, sd = sd(mr3d_acc)) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details ) 
```

#### Attention Score
```{r bis_att}
# Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(bis_att)) %>% 
  filter(session != "1st year") %>% #only 2 ppts at 2nd session>filter out
  ggplot(aes(x = session, y = bis_att, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitter(width = .15), 
                        size = 0.5)  +
  scale_fill_manual(values = c("#43a2ca", "#0868ac")) +
  coord_cartesian(ylim = c(0, 35)) +
  labs(title = "Attention Score on Barratt Impulsivity Scale by Session", 
       x = "Session", y = "Attention Score") )

# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(bis_att)) %>% 
  filter(session != "1st year") %>% #only 2 ppts at 2nd session>filter out
  summarize(mean=mean(bis_att), sd = sd(bis_att), se=std.error(bis_att)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(0, 35)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#43a2ca", "#0868ac")) +
  labs(title = "Attention Score on Barratt Impulsivity Scale by Session", 
       x = "Session", y = "Attention Score")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  filter(!is.na(bis_att)) %>% 
  filter(session != "1st year") %>% #only 2 ppts at 2nd session>filter out
  group_by(session, ppt) %>% 
  summarise(mean = mean(bis_att)) #, sd = sd(mr3d_acc)) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details ) 
```

#### Motor Score
```{r bis_mot}
# Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(bis_mot)) %>% 
  filter(session != "1st year") %>% #only 2 ppts at 2nd session>filter out
  ggplot(aes(x = session, y = bis_mot, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitter(width = .15), 
                        size = 0.5)  +
  scale_fill_manual(values = c("#43a2ca", "#0868ac")) +
  coord_cartesian(ylim = c(0, 35)) +
  labs(title = "Motor Score on Barratt Impulsivity Scale by Session", 
       x = "Session", y = "Motor Score") )

# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(bis_mot)) %>% 
  filter(session != "1st year") %>% #only 2 ppts at 2nd session>filter out
  summarize(mean=mean(bis_mot), sd = sd(bis_mot), se=std.error(bis_mot)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(0, 35)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#43a2ca", "#0868ac")) +
  labs(title = "Motor Score on Barratt Impulsivity Scale by Session", 
       x = "Session", y = "Motor Score")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  filter(!is.na(bis_mot)) %>% 
  filter(session != "1st year") %>% #only 2 ppts at 2nd session>filter out
  group_by(session, ppt) %>% 
  summarise(mean = mean(bis_mot)) #, sd = sd(mr3d_acc)) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details )  
```

#### Non-planning Score
```{r bis_nplan}
# Raincloud plot
( R1 <- apt %>% 
  filter(!is.na(bis_nplan)) %>% 
  filter(session != "1st year") %>% #only 2 ppts at 2nd session>filter out
  ggplot(aes(x = session, y = bis_nplan, group = session, fill = session)) +
  geom_flat_violin(position = position_nudge(x = .25, y = 0),
                   adjust = 2, trim = TRUE, alpha = 1) +
  geom_point(position = position_jitter(width = .15), 
                        size = 0.5)  +
  scale_fill_manual(values = c("#43a2ca", "#0868ac")) +
  coord_cartesian(ylim = c(0, 35)) +
  labs(title = "Non-planning Score on Barratt Impulsivity Scale by Session", 
       x = "Session", y = "Non-planning Score") )

# Jitter plot
J1 <- apt %>% 
  group_by(session) %>% 
  filter(!is.na(bis_nplan)) %>% 
  filter(session != "1st year") %>% #only 2 ppts at 2nd session>filter out
  summarize(mean=mean(bis_nplan), sd = sd(bis_nplan), se=std.error(bis_nplan)) %>%
  ggplot(aes(x = session, y = mean, fill = session)) +
  coord_cartesian(ylim = c(0, 35)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  theme_minimal() +
  scale_fill_manual(values = c("#43a2ca", "#0868ac")) +
  labs(title = "Non-planning Score on Barratt Impulsivity Scale by Session", 
       x = "Session", y = "Non-planning Score")

limits <- aes(ymax = mean + se, ymin = mean - se)
J2 <- J1 + geom_errorbar(position = position_dodge(), 
                          limits, size = 0.5, width = 0.5)

indiv <- apt %>% 
  filter(!is.na(bis_nplan)) %>% 
  filter(session != "1st year") %>% #only 2 ppts at 2nd session>filter out
  group_by(session, ppt) %>% 
  summarise(mean = mean(bis_nplan)) #, sd = sd(mr3d_acc)) # requires trial-level data

J3 <- J2 + geom_point(data=indiv, aes(group = ppt), size = 0.8, 
                       shape = 19, position = pd) +
    geom_line(data = indiv, aes(group = ppt),
                      size = 0.1, position = pd)

( J4 <- J3 + theme_details ) 
```

# Models
Does performance on these cognitive and linguistic assessments change over time?

## Dual N-Back
```{r nback-mdl}
# Does session predict Dual N-Back results?
( nback_comb_mdl <- lm(nback_comb ~ session, 
                  data = apt) ) 

summary(nback_comb_mdl)

( nback_lett_mdl <- lm(nback_lett ~ session, 
                  data = apt) ) 

summary(nback_lett_mdl)

( nback_spat_mdl <- lm(nback_spat ~ session, 
                  data = apt) ) 

summary(nback_spat_mdl)
```

## Corsi Blocks
```{r corsi-mdl}
# Does session predict Corsi Blocks results?
( corsi_corr_mdl <- lm(corsi_corr ~ session, 
                  data = apt) ) 

summary(corsi_corr_mdl)
```

## Kirklees Sentence Reading
```{r kirk-mdl}
# Does session predict Kirklees Sentence Reading results?
( kirk_mdl <- lm(kirk_acc ~ session, 
                 data = apt) ) 

summary(kirk_mdl)
```

## KBIT-2 Matrices
```{r kbit-mdl}
# Does session predict KBIT-2 Matrices results?
( kbit_mdl <- lm(kbit_acc ~ session, 
                  data = apt) ) 

summary(kbit_mdl)
```

## Digit Span
```{r dspan-mdl}
# Does session predict Digit Span results?
( dspan_corr_mdl <- lm(dspan_corr ~ session, 
                  data = apt) ) 

summary(dspan_corr_mdl)

( dspan_mem_mdl <- lm(dspan_mem ~ session, 
                  data = apt) ) 

summary(dspan_mem_mdl)
```

## 2D Mental Rotation
```{r mr2d-mdl}
# Does session predict 2D Mental Rotation results?
( mr2d_sats_mdl <- lm(mr2d_sats ~ session, 
                  data = apt) ) 

summary(mr2d_sats_mdl)

( mr2d_rt_mdl <- lm(mr2d_rt ~ session, 
                  data = apt) ) 

summary(mr2d_rt_mdl)

apt2 <- apt %>% 
  filter(ppt != "HW025") 

( mr2d_rt_mdl2 <- lm(mr2d_rt ~ session, 
                  data = apt2) ) 

summary(mr2d_rt_mdl2)
```

## 3D Mental Rotation
```{r mr3d-mdl}
# Does session predict 3D Mental Rotation results?
( mr3d_sats_mdl <- lm(mr3d_sats ~ session, 
                  data = apt) ) 

summary(mr3d_sats_mdl)

( mr3d_acc_mdl <- lm(mr3d_acc ~ session, 
                  data = apt) ) 

summary(mr3d_acc_mdl)

( mr3d_rt_mdl <- lm(mr3d_rt ~ session, 
                  data = apt) ) 

summary(mr3d_rt_mdl)
```

## Barratt Impulsivity Scale
```{r bis-mdl}
# relevel session because data only for 2nd year vs 3rd year
apt$session <- fct_relevel(apt$session, "2nd year", after = 0)

# Does session predict Barratt Impulsivity Scale results?
( bis_mdl <- lm(bis_tot ~ session, 
                  data = apt) ) 

summary(bis_mdl)
# relevel back again 
apt$session <- fct_relevel(apt$session, "2nd year", after = 2)
```