---
title: "Sign Language Interpreter Aptitude"
subtitle: "03 - BSL/SLI predictors analysis"
author:
  - name: "Freya Watkins"
    affiliation: "University of Birmingham"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    number_sections: false
    theme: flatly
    highlight: haddock
---
# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = TRUE, cache = FALSE) 
```

## Load packages
```{r load_packages}
library(here) # file organisation & folder location
library(tidyverse) # data wrangling & plotting
library(scales) # scales on plots
library(patchwork) # for combining plots
library(lme4) # for linear mixed models
library(sjPlot) # for lmm output
```

### R / package versions used
```{r r_package_version}
R.Version() 
packageVersion('here')
packageVersion('tidyverse')
packageVersion('scales') 
packageVersion('patchwork')
packageVersion('lme4') 
packageVersion('sjPlot') 
```

## Read pre-wrangled data 
(see `00-wrangling-setup.Rmd` script)
```{r read_in_data}
# here::here()
apt <- readRDS(here("data", "apt-data.rds"))
apt <- as_tibble(apt)
head(apt)
```

Filter out participants who did not progress beyond interview
```{r}
apt <- apt %>% filter(selection == "selected")
```

Filter out participants with deaf family members / L1 BSL
```{r}
apt <- apt %>% filter(L1_bsl != 1)
```

Convert data from long format to wide format
```{r}
apt_wide <- apt %>% 
  tidyr::pivot_wider(names_from = session,
                     values_from = c(nback_lett:grade_terp))
```

# Plots & correlations
```{r plot-theme}
# set up a theme for the plots
theme_details <- theme_bw() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(colour = "black", size = 0.5),
    plot.title = element_text(size = 15, face = "bold"),
    plot.title.position = "plot",
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.text.x = element_text(size = 14, colour = "black"),
    axis.text.y = element_text(size = 14, colour = "black"),
    legend.position = "none"
  )
```

### BSL: predicted impact
First we look at the predictor variables which we hypothesised may have a relationship with BSL outcomes.

#### Corsi Blocks

##### vs BSL Grades
```{r corsi_bsl_grades}
# Initial visuospatial skill vs. 1st year BSL grades
apt_wide %>%
  ggplot(aes(x = `corsi_corr_pre-degree`, y = `grade_bsl_1st year`)) +
  geom_point(size = 2) +
  geom_smooth(method = "lm") +
  theme_minimal() +
  theme_details +
  labs(
    title = "Initial visuospatial skill vs. 1st year BSL grades",
    y = "1st year BSL grade",
    x = "Initial Corsi Blocks score"
  )

a <- apt_wide %>% 
  filter(`corsi_corr_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") 

# correlation
a %>% summarize(RSq=(cor(`corsi_corr_pre-degree`, 
                       `grade_bsl_1st year`))^2)

# Initial visuospatial skill vs. 2nd year BSL grades
apt_wide %>%
  ggplot(aes(x = `corsi_corr_pre-degree`, y = `grade_bsl_2nd year`)) +
  geom_smooth(method= "lm") +
  geom_point(size = 2) +
  theme_minimal() + theme_details + 
  labs(title = "Initial visuospatial skill vs. 2nd year BSL grades", 
       y = "2nd year BSL grade", 
       x = "Initial Corsi Blocks score")

#correlation
apt_wide %>% 
  filter(`corsi_corr_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`corsi_corr_pre-degree`, 
                       `grade_bsl_2nd year`))^2)

# 1st year visuospatial skill vs. 1st year BSL grades
apt_wide %>%
  ggplot(aes(x = `corsi_corr_1st year`, y = `grade_bsl_1st year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title = "1st year visuospatial skill vs. 1st year BSL grades", 
       y = "1st year BSL grade", 
       x = "1st year Corsi Blocks score ")

# correlation
apt_wide %>% 
  filter(`corsi_corr_1st year`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(RSq=(cor(`corsi_corr_1st year`, 
                       `grade_bsl_1st year`))^2)

# 1st year visuospatial skill vs. 2nd year BSL grades
apt_wide %>%
  ggplot(aes(x = `corsi_corr_1st year`, y = `grade_bsl_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title = "1st year visuospatial skill vs. 2nd year BSL grades", 
       y = "1st year BSL grade", 
       x = "2nd year Corsi Blocks score ")

# correlation
apt_wide %>% 
  filter(`corsi_corr_1st year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`corsi_corr_1st year`, 
                       `grade_bsl_2nd year`))^2)

# 2nd year visuospatial skill vs. 2nd year BSL grades
apt_wide %>%
  ggplot(aes(x = `corsi_corr_2nd year`, y = `grade_bsl_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(7, 10)) +
  theme_minimal() + theme_details + 
  labs(title = "2nd year visuospatial skill vs. 2nd year BSL grades", 
       y = "2nd year BSL grade", 
       x = "2nd year Corsi Blocks score ")

# correlation
apt_wide %>% 
  filter(`corsi_corr_2nd year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>%
  summarize(RSq=(cor(`corsi_corr_2nd year`, 
                       `grade_bsl_2nd year`))^2)
```

##### vs BSL-SRT
Does Corsi Blocks performance relate to BSL Sentence Reproduction Task?
``` {r corsi_srt}
# Initial Corsi Blocks score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `corsi_corr_pre-degree`, y = `bsl_srt_3rd year`)) +
  geom_smooth(method= "lm") +
  geom_point(size = 2) +
  coord_cartesian(xlim = c(6, 10)) +
  theme_minimal() + theme_details + 
  labs(title = "Initial Corsi Blocks score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", 
       x = "Initial Corsi Blocks score")

# correlation
apt_wide %>% 
  filter(`corsi_corr_pre-degree`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`corsi_corr_pre-degree`, 
                       `bsl_srt_3rd year`))^2)

# 2nd year Corsi Blocks score vs. 3rd year BSL-SRT scores
( fig4a <- apt_wide %>%
  ggplot(aes(x = `corsi_corr_2nd year`, y = `bsl_srt_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title = "a) 2nd year Visuospatial WM vs. 3rd year BSL-SRT score", 
       y = "3rd year BSL-SRT score", 
       x = "2nd year Corsi Blocks score") )

# correlation
apt_wide %>% 
  filter(`corsi_corr_2nd year`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`corsi_corr_2nd year`, 
                       `bsl_srt_3rd year`))^2)

# linear model
lm(`bsl_srt_3rd year` ~ `corsi_corr_2nd year` + self_rating,
                  data = apt_wide) %>% summary()

# 3rd year Corsi Blocks score vs. 3rd year BSL-SRT scores
( fig4b <- apt_wide %>%
  ggplot(aes(x = `corsi_corr_3rd year`, y = `bsl_srt_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title = "b) 3rd year Visuospatial WM vs. 3rd year BSL-SRT score", 
       y = "3rd year BSL-SRT score", 
       x = "3rd year Corsi Blocks score") )

# correlation
apt_wide %>% 
  filter(`corsi_corr_3rd year`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`corsi_corr_3rd year`, 
                       `bsl_srt_3rd year`))^2)

# linear model
lm(`bsl_srt_3rd year` ~ `corsi_corr_3rd year` +
                    self_rating, data = apt_wide) %>% summary()
```

Combine plots for Figure 4 using patchwork:
```{r}
( fig4 <- (fig4a | fig4b) )
ggsave("plots/fig4.jpeg", plot=fig4, width = 12, height = 5, units = "in")
```

#### 2D Mental Rotation

##### vs BSL Grades
Does 2D Mental Rotation performance relate to BSL grades?
``` {r mr2d_bsl_grades}
# Initial 2D Mental Rotation score vs. 1st year BSL grades
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_pre-degree`, y = `grade_bsl_1st year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  theme_minimal() + theme_details + 
  labs(title = "Initial 2D Mental Rotation score vs. 1st year BSL grades", 
       y = "1st year BSL grade", 
       x = "Initial 2D Mental Rotation score")

# correlation
apt_wide %>% 
  filter(`mr2d_sats_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(RSq=(cor(`mr2d_sats_pre-degree`, 
                       `grade_bsl_1st year`))^2)

# Initial 2D Mental Rotation score vs. 2nd year BSL grades
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_pre-degree`, y = `grade_bsl_2nd year`)) +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  geom_point(size = 2) +
  theme_minimal() + theme_details + 
  labs(title = "Initial 2D Mental Rotation score vs. 2nd year BSL grades", 
       y = "2nd year BSL grade", 
       x = "Initial 2D Mental Rotation score")

# correlation
apt_wide %>% 
  filter(`mr2d_sats_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`mr2d_sats_pre-degree`, 
                       `grade_bsl_2nd year`))^2)

# 1st year 2D Mental Rotation score vs. 1st year BSL grades
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_1st year`, y = `grade_bsl_1st year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  theme_minimal() + theme_details + 
  labs(title = "1st year 2D Mental Rotation score vs. 1st year BSL grades", 
       y = "1st year BSL grade", 
       x = "1st year 2D Mental Rotation score")

# correlation
apt_wide %>% 
  filter(`mr2d_sats_1st year`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(RSq=(cor(`mr2d_sats_1st year`, 
                       `grade_bsl_1st year`))^2)

# linear model
lm(`grade_bsl_1st year` ~ `mr2d_sats_1st year` + self_rating,
                  data = apt_wide) %>% summary()
# interestingly, a negative correlation, but not significant

# 1st year 2D Mental Rotation score vs. 2nd year BSL grades
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_1st year`, y = `grade_bsl_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  theme_minimal() + theme_details + 
  labs(title = "1st year 2D Mental Rotation score vs. 2nd year BSL grades", 
       y = "1st year BSL grade", 
       x = "2nd year 2D Mental Rotation score")

# correlation
apt_wide %>% 
  filter(`mr2d_sats_1st year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`mr2d_sats_1st year`, 
                       `grade_bsl_2nd year`))^2)

# 2nd year 2D Mental Rotation score vs. 2nd year BSL grades
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_2nd year`, y = `grade_bsl_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  coord_cartesian(xlim = c(-1.3, 1.3)) +
  theme_minimal() + theme_details + 
  labs(title = "2nd year 2D Mental Rotation vs. 2nd year BSL Grades", 
       y = "2nd year BSL Grades", 
       x = "2nd year 2D Mental Rotation score")

# correlation
apt_wide %>% 
  filter(`mr2d_sats_2nd year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>%   
  summarize(RSq=(cor(`mr2d_sats_2nd year`, 
                       `grade_bsl_2nd year`))^2)

# linear model
lm(`grade_bsl_2nd year` ~ `mr2d_sats_2nd year` +
                   self_rating, data = apt_wide) %>% summary()
```

##### vs BSL-SRT
Does 2D Mental Rotation performance relate to BSL Sentence Reproduction Task?
``` {r mr2d_bsl_srt}
# 2nd year 2D Mental Rotation score vs. 2nd year BSL-SRT scores
# just 4 data points here

# 3rd year 2D Mental Rotation score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_3rd year`, y = `bsl_srt_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  theme_minimal() + theme_details + 
  labs(title = "3rd year 2D Mental Rotation score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", 
       x = "3rd year 2D Mental Rotation score")

# correlation
apt_wide %>% 
  filter(`mr2d_sats_3rd year`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`mr2d_sats_3rd year`, 
                       `bsl_srt_3rd year`))^2)

# linear model
lm(`bsl_srt_3rd year` ~ `mr2d_sats_3rd year` +
                   self_rating, data = apt_wide) %>% summary()
```

#### 3D Mental Rotation 

##### vs BSL Grades
Does 3D Mental Rotation performance relate to BSL grades?
``` {r mr3d_bsl_grades}
# Initial 3D Mental Rotation score vs. 1st year BSL grades
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_pre-degree`, y = `grade_bsl_1st year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  theme_minimal() + theme_details + 
  labs(title = "Initial 3D Mental Rotation score vs. 1st year BSL grades", 
       y = "1st year BSL grade", 
       x = "Initial 3D Mental Rotation score")

# correlation
apt_wide %>% 
  filter(`mr3d_sats_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(RSq=(cor(`mr3d_sats_pre-degree`, 
                       `grade_bsl_1st year`))^2)

# linear model
lm(`grade_bsl_1st year` ~ `mr3d_sats_pre-degree` +
                   self_rating, data = apt_wide) %>% summary()

# Initial 3D Mental Rotation score vs. 2nd year BSL grades
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_pre-degree`, y = `grade_bsl_2nd year`)) +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  geom_point(size = 2) +
  theme_minimal() + theme_details + 
  labs(title = "Initial 3D Mental Rotation score vs. 2nd year BSL grades", 
       y = "2nd year BSL grade", 
       x = "Initial 3D Mental Rotation score")

# correlation
apt_wide %>% 
  filter(`mr3d_sats_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`mr3d_sats_pre-degree`, 
                       `grade_bsl_2nd year`))^2)

# 2nd year 3D Mental Rotation score vs. 2nd year BSL grades
( fig5b <- apt_wide %>%
  ggplot(aes(x = `mr3d_sats_2nd year`, y = `grade_bsl_2nd year`)) +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(-1.2, 2.6)) +
  theme_minimal() + theme_details + 
  labs(title = "b) 2nd year 3D Mental Rotation vs. 2nd year BSL Grade", 
       y = "2nd year BSL Grade", 
       x = "2nd year 3D Mental Rotation score") )

# correlation
apt_wide %>% 
  filter(`mr3d_sats_2nd year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>%   
  summarize(RSq=(cor(`mr3d_sats_2nd year`, 
                       `grade_bsl_2nd year`))^2)

# linear model
lm(`grade_bsl_2nd year` ~ `mr3d_sats_2nd year` +
                   self_rating, data = apt_wide) %>% summary()
```

##### vs BSL-SRT
Does 3D Mental Rotation performance relate to BSL Sentence Reproduction Task?
``` {r mr3d_bsl_srt}
# Initial 3D Mental Rotation score vs. 3rd year BSL-SRT scores
( fig5a <- apt_wide %>%
  ggplot(aes(x = `mr3d_sats_pre-degree`, y = `bsl_srt_3rd year`)) +
  geom_point(size = 2) +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(-2.7, 1.2)) +
  theme_minimal() + theme_details + 
  labs(title = "a) Initial 3D Mental Rotation vs. 3rd year BSL-SRT", 
       y = "3rd year BSL-SRT score", 
       x = "Initial 3D Mental Rotation score") )

# correlation
apt_wide %>% 
  filter(`mr3d_sats_pre-degree`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`mr3d_sats_pre-degree`, 
                       `bsl_srt_3rd year`))^2)

lm(`bsl_srt_3rd year` ~ `mr3d_sats_pre-degree` +
                   self_rating, data = apt_wide) %>% summary()

# 2nd year 3D Mental Rotation score vs. 2nd year BSL-SRT scores
# only 4 data points here

# 3rd year 3D Mental Rotation score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_3rd year`, y = `bsl_srt_3rd year`)) +
  geom_point(size = 2) +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title = "3rd year 3D Mental Rotation score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", 
       x = "3rd year 3D Mental Rotation score")

# correlation
apt_wide %>% 
  filter(`mr3d_sats_3rd year`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`mr3d_sats_3rd year`, 
                       `bsl_srt_3rd year`))^2)
```
Combine plots for Figure 5 using patchwork:
```{r}
( fig5 <- (fig5a | fig5b) )
ggsave("plots/fig5.jpeg", plot=fig5, width = 12, height = 5, units = "in")
```

#### MLAT Number Learning
##### vs BSL Grades
```{r mlat_grade_bsl}
# Initial MLAT Number Learning Accuracy vs. BSL grades 1st year
apt_wide %>%
  filter(`mlat_acc_pre-degree` != "na") %>% 
  filter(`grade_bsl_1st year` != "na") %>% 
  ggplot(aes(x = `mlat_acc_pre-degree`, y = `grade_bsl_1st year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title= "Initial MLAT Number Learning Accuracy vs. BSL grades 1st year", 
       x = "MLAT Number Learning Accuracy", y = "BSL grade 1st year")

# correlation
apt_wide %>% 
  filter(`mlat_acc_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(RSq=(cor(`mlat_acc_pre-degree`, 
                       `grade_bsl_1st year`))^2)

# linear model
lm(`grade_bsl_1st year` ~ `mlat_acc_pre-degree` +
                   self_rating, data = apt_wide) %>% summary()

# Initial MLAT Number Learning Accuracy vs. BSL grades 2nd year
apt_wide %>%
  filter(`mlat_acc_pre-degree` != "na") %>% 
  filter(`grade_bsl_2nd year` != "na") %>% 
  ggplot(aes(x = `mlat_acc_pre-degree`, y = `grade_bsl_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title= "Initial MLAT Number Learning Accuracy vs. BSL grades 2nd year", 
       x = "MLAT Number Learning Accuracy", y = "BSL grade 2nd year")

# correlation
apt_wide %>% 
  filter(`mlat_acc_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`mlat_acc_pre-degree`, 
                       `grade_bsl_2nd year`))^2)

# linear model
lm(`grade_bsl_2nd year` ~ `mlat_acc_pre-degree` +
                   self_rating, data = apt_wide) %>% summary()
```

##### vs BSL-SRT
```{r mlat_bsl-srt}
# Initial MLAT Number Learning Accuracy vs. BSL-SRT 3rd year
apt_wide %>%
  filter(`mlat_acc_pre-degree` != "na") %>% 
  filter(`bsl_srt_3rd year` != "na") %>% 
  ggplot(aes(x = `mlat_acc_pre-degree`, y = `bsl_srt_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title= "Initial MLAT Number Learning Accuracy vs. BSL-SRT score 3rd year", 
       x = "MLAT Number Learning Accuracy")

# correlation
apt_wide %>% 
  filter(`mlat_acc_pre-degree`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`mlat_acc_pre-degree`, 
                       `bsl_srt_3rd year`))^2)
```

### BSL: no predicted impact
Now we look at the predictor variables which we hypothesised were unlikely to have a relationship with BSL outcomes.

#### Kirklees Sentence Reading

##### vs BSL Grades
```{r kirk_acc_grade_bsl}
# Kirklees Sentence Reading pre-degree vs. BSL grades 1st year
( fig6a <- apt_wide %>%
  ggplot(aes(x = `kirk_acc_pre-degree`, y = `grade_bsl_1st year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  coord_cartesian(xlim = c(.49, .96)) +
  theme_minimal() + theme_details + 
  labs(title = "a) Initial English vocab vs. 1st year BSL Grade", 
       y = "1st year BSL Grade", x = "Initial Kirklees accuracy") )

# correlation
apt_wide %>% 
  filter(`kirk_acc_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(RSq=(cor(`kirk_acc_pre-degree`, 
                       `grade_bsl_1st year`))^2)

# linear model
kirk0_bsl1 <- lm(`grade_bsl_1st year` ~ `kirk_acc_pre-degree` +
                   self_rating# + age_s1 # removing age for public version of code
                 , data = apt_wide)
summary(kirk0_bsl1)
tab_model(kirk0_bsl1, show.aic = T)

# Kirklees Sentence Reading pre-degree vs. BSL grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_pre-degree`, y = `grade_bsl_2nd year`)) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(.55, .95)) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  geom_point(size = 2) +
  theme_minimal() + theme_details + 
  labs(title = "Kirklees Sentence Reading pre-degree vs. BSL grades 2nd year", 
       y = "2nd year BSL grade", x = "Kirklees Sentence Reading pre-degree")

# correlation
apt_wide %>% 
  filter(`kirk_acc_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`kirk_acc_pre-degree`, 
                       `grade_bsl_2nd year`))^2)

# Kirklees Sentence Reading 1st year vs. BSL grades 1st year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_1st year`, y = `grade_bsl_1st year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "Kirklees Sentence Reading 1st year vs. BSL grades 1st year", 
       y = "1st year BSL grade", x = "Kirklees Sentence Reading after 1 year")

# correlation
apt_wide %>% 
  filter(`kirk_acc_1st year`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(RSq=(cor(`kirk_acc_1st year`, 
                       `grade_bsl_1st year`))^2)

# Kirklees Sentence Reading 1st year vs. BSL grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_1st year`, y = `grade_bsl_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "Kirklees Sentence Reading 1st year vs. BSL grades 2nd year", 
       y = "2nd year BSL grade", x = "Kirklees Sentence Reading after 1 year")

# correlation
apt_wide %>% 
  filter(`kirk_acc_1st year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`kirk_acc_1st year`, 
                       `grade_bsl_2nd year`))^2)

# Kirklees Sentence Reading 2nd year vs. BSL grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_2nd year`, y = `grade_bsl_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(.6, 1)) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "Kirklees Sentence Reading 2nd year vs. BSL grades 2nd year", 
       y = "2nd year BSL grade", x = "Kirklees Sentence Reading 2nd year")

# correlation
apt_wide %>% 
  filter(`kirk_acc_2nd year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>%
  summarize(RSq=(cor(`kirk_acc_2nd year`, 
                       `grade_bsl_2nd year`))^2)
```
##### vs BSL-SRT
Does Kirklees Sentence Reading performance relate to BSL Sentence Reproduction Task?
``` {r kirk_bsl_srt}
# Initial Kirklees Sentence Reading score vs. 3rd year BSL-SRT scores
( fig6b <- apt_wide %>%
  ggplot(aes(x = `kirk_acc_pre-degree`, y = `bsl_srt_3rd year`)) +
  geom_point(size = 2, position="jitter", seed = 42) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  coord_cartesian(xlim = c(.56, .93)) +
  theme_minimal() + theme_details + 
  labs(title = "b) Initial English vocab vs. 3rd year BSL-SRT score", 
       y = "3rd year BSL-SRT score", x = "Initial Kirklees accuracy") )

# correlation
apt_wide %>% 
  filter(`kirk_acc_pre-degree`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`kirk_acc_pre-degree`, 
                       `bsl_srt_3rd year`))^2)

lm(`bsl_srt_3rd year` ~ `kirk_acc_pre-degree` +
                   self_rating, data = apt_wide) %>% summary()

# 2nd year Kirklees Sentence Reading score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `kirk_acc_2nd year`, y = `bsl_srt_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title = "2nd year Kirklees Sentence Reading score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", x = "2nd year Kirklees Sentence Reading score")

# correlation
apt_wide %>% 
  filter(`kirk_acc_2nd year`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`kirk_acc_2nd year`, 
                       `bsl_srt_3rd year`))^2)
```

Combine plots for Figure 6 using patchwork:
```{r}
( fig6 <- (fig6a | fig6b) )
ggsave("plots/fig6.jpeg", plot=fig6, width = 12, height = 5, units = "in")
```

#### Summarising Task

##### vs BSL Grades
```{r summ_grade_bsl}
# Summarising pre-degree vs. BSL Grades 1st year
apt_wide %>%
  ggplot(aes(x = `summ_pre-degree`, y = `grade_bsl_1st year`)) +
  geom_smooth(method= "lm") +
  geom_point(size = 2) +
  theme_minimal() + theme_details + 
  labs(title = "Summarising pre-degree vs. BSL Grades 1st year", 
       y = "1st year BSL grade", x = "Summarising pre-degree")

# correlation
apt_wide %>% 
  filter(`summ_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(RSq=(cor(`summ_pre-degree`, 
                       `grade_bsl_1st year`))^2)

# Summarising pre-degree vs. BSL Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `summ_pre-degree`, y = `grade_bsl_2nd year`)) +
  geom_smooth(method= "lm") +
  geom_point(size = 2) +
  theme_minimal() + theme_details + 
  labs(title = "Summarising pre-degree vs. BSL Grades 2nd year", 
       y = "2nd year BSL grade", x = "Summarising pre-degree")

# correlation
apt_wide %>% 
  filter(`summ_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`summ_pre-degree`, 
                       `grade_bsl_2nd year`))^2)
```

##### vs BSL-SRT
```{r summ_bsl-srt}
# Summarising pre-degree vs. BSL-SRT 3rd year
apt_wide %>%
  ggplot(aes(x = `summ_pre-degree`, y = `bsl_srt_3rd year`)) +
  geom_smooth(method= "lm") +
  geom_point(size = 2) +
  theme_minimal() + theme_details + 
  labs(title = "Summarising pre-degree vs. BSL-SRT 3rd year", 
       y = "BSL-SRT 3rd year", x = "Summarising pre-degree")

# correlation
apt_wide %>% 
  filter(`summ_pre-degree`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`summ_pre-degree`, 
                       `bsl_srt_3rd year`))^2)
```

#### KBIT-2 Matrices 

##### vs BSL Grades
```{r kbit_acc_grade_bsl}
# KBIT-2 Matrices pre-degree vs. BSL grades 1st year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_pre-degree`, y = `grade_bsl_1st year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "KBIT-2 Matrices pre-degree vs. BSL grades 1st year", 
       y = "1st year BSL grade", x = "KBIT-2 Matrices pre-degree")

# correlation
apt_wide %>% 
  filter(`kbit_acc_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(RSq=(cor(`kbit_acc_pre-degree`, 
                       `grade_bsl_1st year`))^2)

# KBIT-2 Matrices pre-degree vs. BSL grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_pre-degree`, y = `grade_bsl_2nd year`)) +
  geom_smooth(method= "lm") +
  geom_point(size = 2) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "KBIT-2 Matrices pre-degree vs. BSL grades 2nd year", 
       y = "2nd year BSL grade", x = "KBIT-2 Matrices pre-degree")

# correlation
apt_wide %>% 
  filter(`kbit_acc_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`kbit_acc_pre-degree`, 
                       `grade_bsl_2nd year`))^2)

# KBIT-2 Matrices 1st year vs. BSL grades 1st year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_1st year`, y = `grade_bsl_1st year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "KBIT-2 Matrices 1st year vs. BSL grades 1st year", 
       y = "1st year BSL grade", x = "KBIT-2 Matrices 1st year")

# correlation
apt_wide %>% 
  filter(`kbit_acc_1st year`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(RSq=(cor(`kbit_acc_1st year`, 
                       `grade_bsl_1st year`))^2)

# KBIT-2 Matrices 1st year vs. BSL grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_1st year`, y = `grade_bsl_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "KBIT-2 Matrices 1st year vs. BSL grades 2nd year", 
       y = "2nd year BSL grade", x = "KBIT-2 Matrices 1st year")

# correlation
apt_wide %>% 
  filter(`kbit_acc_1st year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`kbit_acc_1st year`, 
                       `grade_bsl_2nd year`))^2)

# KBIT-2 Matrices 2nd year vs. BSL grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_2nd year`, y = `grade_bsl_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "KBIT-2 Matrices 2nd year vs. BSL grades 2nd year", 
       y = "2nd year BSL grade", x = "KBIT-2 Matrices 2nd year")

# correlation
apt_wide %>% 
  filter(`kbit_acc_2nd year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>%
  summarize(RSq=(cor(`kbit_acc_2nd year`, 
                       `grade_bsl_2nd year`))^2)
```

##### vs BSL-SRT
Does KBIT-2 Matrices performance relate to BSL Sentence Reproduction Task?
``` {r kbit_bsl_srt}
# Initial KBIT-2 Matrices score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `kbit_acc_pre-degree`, y = `bsl_srt_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(.84, 1)) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "Initial KBIT-2 Matrices score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", x = "Initial KBIT-2 Matrices score")

# correlation
apt_wide %>% 
  filter(`kbit_acc_pre-degree`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`kbit_acc_pre-degree`, 
                       `bsl_srt_3rd year`))^2)

# 2nd year KBIT-2 Matrices score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `kbit_acc_2nd year`, y = `bsl_srt_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "2nd year KBIT-2 Matrices score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", x = "2nd year KBIT-2 Matrices score")

# correlation
apt_wide %>% 
  filter(`kbit_acc_2nd year`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`kbit_acc_2nd year`, 
                       `bsl_srt_3rd year`))^2)
```

#### Dual N-Back 

##### vs BSL Grades
```{r nback_bsl_grade}
# Dual N-Back pre-degree vs. BSL Grades 1st year
apt_wide %>%
  ggplot(aes(x = `nback_comb_pre-degree`, y = `grade_bsl_1st year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = " Dual N-Back pre-degree vs. BSL Grades 1st year", 
       y = "1st year BSL grade", x = "Dual N-Back pre-degree")

# correlation
apt_wide %>% 
  filter(`nback_comb_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(RSq=(cor(`nback_comb_pre-degree`, 
                       `grade_bsl_1st year`))^2)

# Dual N-Back pre-degree vs. BSL Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `nback_comb_pre-degree`, y = `grade_bsl_2nd year`)) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  geom_point(size = 2) +
  theme_minimal() + theme_details + 
  labs(title = " Dual N-Back pre-degree vs. BSL Grades 2nd year", 
       y = "2nd year BSL grade", x = "Dual N-Back pre-degree")

# correlation
apt_wide %>% 
  filter(`nback_comb_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`nback_comb_pre-degree`, 
                       `grade_bsl_2nd year`))^2)

# Dual N-Back 2nd year vs. BSL Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `nback_comb_2nd year`, y = `grade_bsl_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = " Dual N-Back 2nd year vs. BSL Grades 2nd year", 
       y = "2nd year BSL grade", x = "Dual N-Back 2nd year")

# correlation
apt_wide %>% 
  filter(`nback_comb_2nd year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>%   
  summarize(RSq=(cor(`nback_comb_2nd year`, 
                       `grade_bsl_2nd year`))^2)
```
##### vs BSL-SRT
Does Dual N-Back performance relate to BSL Sentence Reproduction Task?
``` {r nback_srt}
# Initial Dual N-Back score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `nback_comb_pre-degree`, y = `bsl_srt_3rd year`)) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(.71, .75)) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  geom_point(size = 2) +
  theme_minimal() + theme_details + 
  labs(title = "Initial Dual N-Back score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", 
       x = "Initial Dual N-Back score")

# correlation
apt_wide %>% 
  filter(`nback_comb_pre-degree`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`nback_comb_pre-degree`, 
                       `bsl_srt_3rd year`))^2)

# 2nd year Dual N-Back score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `nback_comb_2nd year`, y = `bsl_srt_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "2nd year Dual N-Back score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", 
       x = "2nd year Dual N-Back score")

# correlation
apt_wide %>% 
  filter(`nback_comb_2nd year`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`nback_comb_2nd year`, 
                       `bsl_srt_3rd year`))^2)

# 3rd year Dual N-Back score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `nback_comb_3rd year`, y = `bsl_srt_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "3rd year Dual N-Back score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", 
       x = "3rd year Dual N-Back score")

# correlation
apt_wide %>% 
  filter(`nback_comb_3rd year`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`nback_comb_3rd year`, 
                       `bsl_srt_3rd year`))^2)

# linear model
lm(`bsl_srt_3rd year` ~ `nback_comb_3rd year` +
                   self_rating, data = apt_wide) %>% summary()
```

#### Digit Span 
##### vs BSL Grades
```{r dspan_bsl}
# Digit Span pre-degree vs. BSL grades 1st year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_pre-degree`, y = `grade_bsl_1st year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "Digit Span pre-degree vs. BSL grades 1st year", 
       y = "1st year BSL grade", x = "Digit Span pre-degree")

# correlation
apt_wide %>% 
  filter(`dspan_corr_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>%   
  summarize(RSq=(cor(`dspan_corr_pre-degree`, 
                       `grade_bsl_1st year`))^2)

# Digit Span pre-degree vs. BSL grades 2nd year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_pre-degree`, y = `grade_bsl_2nd year`)) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  geom_point(size = 2) +
  theme_minimal() + theme_details + 
  labs(title = "Digit Span pre-degree vs. BSL grades 2nd year", 
       y = "2nd year BSL grade", x = "Digit Span pre-degree")

# correlation
apt_wide %>% 
  filter(`dspan_corr_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>%   
  summarize(RSq=(cor(`dspan_corr_pre-degree`, 
                       `grade_bsl_2nd year`))^2)

# No datapoints for Digit Span @ '1 year of study'

# Digit Span 2nd year vs. BSL grades 2nd year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_2nd year`, y = `grade_bsl_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "Digit Span 2nd year vs BSL grades 2nd year", 
       y = "2nd year BSL grade", x = "Digit Span 2nd year")

# correlation
apt_wide %>% 
  filter(`dspan_corr_2nd year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>%   
  summarize(RSq=(cor(`dspan_corr_2nd year`, 
                       `grade_bsl_2nd year`))^2)
```

##### vs BSL-SRT
Does Digit Span score relate to BSL-SRT score?
``` {r dspan_bsl_srt}
# Initial Digit Span score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `dspan_corr_pre-degree`, y = `bsl_srt_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(.63, .81)) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "Initial Digit Span score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", x = "Initial Digit Span score")

# correlation
apt_wide %>% 
  filter(`dspan_corr_pre-degree`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`dspan_corr_pre-degree`, 
                       `bsl_srt_3rd year`))^2)

# 2nd year Digit Span score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `dspan_corr_2nd year`, y = `bsl_srt_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(.63, .81)) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "2nd year Digit Span score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", x = "2nd year Digit Span score")

# correlation
apt_wide %>% 
  filter(`dspan_corr_2nd year`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`dspan_corr_2nd year`, 
                       `bsl_srt_3rd year`))^2)
```

#### Barratt Impulsiveness Scale 
##### vs BSL Grades
```{r bis_grade_bsl}
# Barratt Impulsiveness Scale 2nd year vs BSL grades 1st year
apt_wide %>%
  filter(`bis_tot_2nd year` != "na") %>% 
  filter(`grade_bsl_1st year` != "na") %>% 
  ggplot(aes(x = `bis_tot_2nd year`, y = `grade_bsl_1st year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title= "Impulsivity vs. BSL grades 1st year", 
       y = "1st year BSL grade", x = "BIS 2nd year")

# correlation
apt_wide %>% 
  filter(`bis_tot_2nd year`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(RSq=(cor(`bis_tot_2nd year`, 
                       `grade_bsl_1st year`))^2)

# Barratt Impulsiveness Scale 2nd year vs BSL grades 2nd year
apt_wide %>%
  filter(`bis_tot_2nd year` != "na") %>% 
  filter(`grade_bsl_2nd year` != "na") %>% 
  ggplot(aes(x = `bis_tot_2nd year`, y = `grade_bsl_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title= "Impulsivity vs. BSL grades 2nd year", 
       y = "2nd year BSL grade", x = "BIS 2nd year")

# correlation
apt_wide %>% 
  filter(`bis_tot_2nd year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`bis_tot_2nd year`, 
                       `grade_bsl_2nd year`))^2)

# Barratt Impulsiveness Scale 2nd year vs BSL self-rated proficiency
apt_wide %>%
  filter(`bis_tot_2nd year` != "na") %>% 
  filter(self_rating != "na") %>% 
  ggplot(aes(x = `bis_tot_2nd year`, y = self_rating)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title= "Impulsivity vs. Initial BSL self-rating", 
       y = "Initial BSL self-rating", x = "BIS 2nd year")
```

##### vs BSL-SRT
```{r bis_bsl_srt}
# Barratt Impulsiveness Scale 2nd year vs BSL-SRT 3rd year
apt_wide %>%
  filter(`bis_tot_2nd year` != "na") %>% 
  filter(`bsl_srt_3rd year` != "na") %>% 
  ggplot(aes(x = `bis_tot_2nd year`, y = `bsl_srt_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title= "Impulsivity 2nd year vs. BSL-SRT 3rd year", 
       y = "3rd year BSL-SRT score", x = "BIS Score 2nd year")

# correlation
apt_wide %>% 
  filter(`bis_tot_2nd year`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`bis_tot_2nd year`, 
                       `bsl_srt_3rd year`))^2)

# linear model
lm(`bsl_srt_3rd year` ~ `bis_tot_2nd year` +
                   self_rating, data = apt_wide) %>% summary()
```
#################################
### Interpreting: predicted impact
Now we turn to look at the predictor variables which we hypothesised may have a relationship with SLI outcomes.

#### Dual N-Back 

##### vs Interpreting Grades
```{r nback_terp_grade}
# Dual N-Back pre-degree vs. Interpreting Grades 1st year
apt_wide %>%
  ggplot(aes(x = `nback_comb_pre-degree`, y = `grade_terp_1st year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(.71, .75)) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = " Dual N-Back pre-degree vs. Interpreting Grades 1st year", 
       y = "1st year Interpreting grade", x = "Dual N-Back pre-degree")

# correlation
apt_wide %>% 
  filter(`nback_comb_pre-degree`!= "NA") %>% 
  filter(`grade_terp_1st year` != "NA") %>% 
  summarize(RSq=(cor(`nback_comb_pre-degree`, 
                       `grade_terp_1st year`))^2)

# Dual N-Back pre-degree vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `nback_comb_pre-degree`, y = `grade_terp_2nd year`)) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  geom_point(size = 2) +
  theme_minimal() + theme_details + 
  labs(title = " Dual N-Back pre-degree vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "Dual N-Back pre-degree")

# correlation
apt_wide %>% 
  filter(`nback_comb_pre-degree`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`nback_comb_pre-degree`, 
                       `grade_terp_2nd year`))^2)

# Dual N-Back 2nd year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `nback_comb_2nd year`, y = `grade_terp_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = " Dual N-Back 2nd year vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "Dual N-Back 2nd year")

# correlation
apt_wide %>% 
  filter(`nback_comb_2nd year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>%   
  summarize(RSq=(cor(`nback_comb_2nd year`, 
                       `grade_terp_2nd year`))^2)
```

##### vs Eng>BSL interpreting
```{r nback_e2b_terp}
# Dual N-Back pre-degree vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `nback_comb_pre-degree`, y = `terp_e2b_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(.71, .75)) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = " Dual N-Back pre-degree vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "Dual N-Back pre-degree")

# correlation
apt_wide %>% 
  filter(`nback_comb_pre-degree`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`nback_comb_pre-degree`, 
                       `terp_e2b_3rd year`))^2)

# Dual N-Back 2nd year vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `nback_comb_2nd year`, y = `terp_e2b_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = " Dual N-Back 2nd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "Dual N-Back 2nd year")

# correlation
apt_wide %>% 
  filter(`nback_comb_2nd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`nback_comb_2nd year`, 
                       `terp_e2b_3rd year`))^2)

# Dual N-Back 3rd year vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `nback_comb_3rd year`, y = `terp_e2b_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = " Dual N-Back 3rd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "Dual N-Back 3rd year")

# correlation
apt_wide %>% 
  filter(`nback_comb_3rd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`nback_comb_3rd year`, 
                       `terp_e2b_3rd year`))^2)

# linear model
lm(`terp_e2b_3rd year` ~ `nback_comb_3rd year` +
                   self_rating, data = apt_wide) %>% summary()
```

##### vs BSL>Eng interpreting
```{r nback_b2e_terp}
# Dual N-Back pre-degree vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `nback_comb_pre-degree`, y = `terp_b2e_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(.71, .75)) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = " Dual N-Back pre-degree vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "Dual N-Back pre-degree")

# correlation
apt_wide %>% 
  filter(`nback_comb_pre-degree`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`nback_comb_pre-degree`, 
                       `terp_b2e_3rd year`))^2)

# Dual N-Back 2nd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `nback_comb_2nd year`, y = `terp_b2e_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = " Dual N-Back 2nd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "Dual N-Back 2nd year")

# correlation
apt_wide %>% 
  filter(`nback_comb_2nd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`nback_comb_2nd year`, 
                       `terp_b2e_3rd year`))^2)

# Dual N-Back 3rd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `nback_comb_3rd year`, y = `terp_b2e_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = " Dual N-Back 3rd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "Dual N-Back 3rd year")

# correlation
apt_wide %>% 
  filter(`nback_comb_3rd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`nback_comb_3rd year`, 
                       `terp_b2e_3rd year`))^2)
```

#### Corsi Blocks 
##### vs Interpreting Grades 
```{r corsi_terp}
# Corsi Blocks pre-degree vs. Interpreting Grades 1st year
apt_wide %>%
  ggplot(aes(x = `corsi_corr_pre-degree`, y = `grade_terp_1st year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(8, 10)) +
  theme_minimal() + theme_details + 
  labs(title = "Corsi Blocks pre-degree vs. Interpreting Grades 1st year", 
       y = "1st year Interpreting grade", x = "Corsi Blocks pre-degree")

# correlation
apt_wide %>% 
  filter(`corsi_corr_pre-degree`!= "NA") %>% 
  filter(`grade_terp_1st year` != "NA") %>% 
  summarize(RSq=(cor(`corsi_corr_pre-degree`, 
                       `grade_terp_1st year`))^2)

# Corsi Blocks pre-degree vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `corsi_corr_pre-degree`, y = `grade_terp_2nd year`)) +
  geom_smooth(method= "lm") +
  geom_point(size = 2) +
  theme_minimal() + theme_details + 
  labs(title = "Corsi Blocks pre-degree vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "Corsi Blocks pre-degree")

# correlation
apt_wide %>% 
  filter(`corsi_corr_pre-degree`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`corsi_corr_pre-degree`, 
                       `grade_terp_2nd year`))^2)

# Corsi Blocks 1st year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `corsi_corr_1st year`, y = `grade_terp_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title = "Corsi Blocks 1st year vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "Corsi Blocks 1st year")

# correlation
apt_wide %>% 
  filter(`corsi_corr_1st year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`corsi_corr_1st year`, 
                       `grade_terp_2nd year`))^2)

# Corsi Blocks 2nd year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `corsi_corr_2nd year`, y = `grade_terp_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(7, 10)) +
  theme_minimal() + theme_details + 
  labs(title = "Corsi Blocks 2nd year vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "Corsi Blocks 2nd year")

# correlation
apt_wide %>% 
  filter(`corsi_corr_2nd year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`corsi_corr_2nd year`, 
                       `grade_terp_2nd year`))^2)
```

##### vs Eng>BSL interpreting
```{r corsi_e2b_terp}
#  Corsi Blocks pre-degree vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `corsi_corr_pre-degree`, y = `terp_e2b_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(6, 10)) +
  theme_minimal() + theme_details + 
  labs(title = " Corsi Blocks pre-degree vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "Corsi Blocks pre-degree")

# correlation
apt_wide %>% 
  filter(`corsi_corr_pre-degree`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`corsi_corr_pre-degree`, 
                       `terp_e2b_3rd year`))^2)

# linear model
lm(`terp_e2b_3rd year` ~ `corsi_corr_pre-degree` +
                   self_rating, data = apt_wide) %>% summary()

#  Corsi Blocks 2nd year vs. Eng to BSL interpreting 3rd year
( fig7a <- apt_wide %>%
  ggplot(aes(x = `corsi_corr_2nd year`, y = `terp_e2b_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(7, 11)) +
  theme_minimal() + theme_details + 
  labs(title = "a) 2nd year Visuospatial WM vs. 3rd yr Eng>BSL interp.",
       y = "3rd year Eng>BSL interp. score", 
       x = "2nd year Corsi Blocks score") )

# correlation
apt_wide %>% 
  filter(`corsi_corr_2nd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`corsi_corr_2nd year`, 
                       `terp_e2b_3rd year`))^2)

# linear model
lm(`terp_e2b_3rd year` ~ `corsi_corr_2nd year` +
                   self_rating, data = apt_wide) %>% summary()

#  Corsi Blocks 3rd year vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `corsi_corr_3rd year`, y = `terp_e2b_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title = " Corsi Blocks 3rd yr vs. Eng to BSL interpreting 3rd yr",
       y = "Eng to BSL interpreting 3rd year", x = "Corsi Blocks 3rd year")

# correlation
apt_wide %>% 
  filter(`corsi_corr_3rd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`corsi_corr_3rd year`, 
                       `terp_e2b_3rd year`))^2)
```

##### vs BSL>Eng interpreting
```{r corsi_b2e_terp}
#  Corsi Blocks pre-degree vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `corsi_corr_pre-degree`, y = `terp_b2e_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(6, 10)) +
  theme_minimal() + theme_details + 
  labs(title = " Corsi Blocks pre-degree vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "Corsi Blocks pre-degree")

# correlation
apt_wide %>% 
  filter(`corsi_corr_pre-degree`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`corsi_corr_pre-degree`, 
                       `terp_b2e_3rd year`))^2)

#  Corsi Blocks 2nd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `corsi_corr_2nd year`, y = `terp_b2e_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title = " Corsi Blocks 2nd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "Corsi Blocks 2nd year")

# correlation
apt_wide %>% 
  filter(`corsi_corr_2nd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`corsi_corr_2nd year`, 
                       `terp_b2e_3rd year`))^2)

# linear model
lm(`terp_b2e_3rd year` ~ `corsi_corr_2nd year` +
                   self_rating, data = apt_wide) %>% summary()

#  Corsi Blocks 3rd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `corsi_corr_3rd year`, y = `terp_b2e_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title = " Corsi Blocks 3rd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "Corsi Blocks 3rd year")

# correlation
apt_wide %>% 
  filter(`corsi_corr_3rd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`corsi_corr_3rd year`, 
                       `terp_b2e_3rd year`))^2)
```

#### Digit Span 

##### vs Interpreting Grades
```{r dspan_grade_terp}
# Digit Span pre-degree vs. Interpreting Grades 1st year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_pre-degree`, y = `grade_terp_1st year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(.6, .81)) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "Digit Span pre-degree vs. Interpreting Grades 1st year", 
       y = "1st year Interpreting grade", x = "Digit Span pre-degree")

# correlation
apt_wide %>% 
  filter(`dspan_corr_pre-degree`!= "NA") %>% 
  filter(`grade_terp_1st year` != "NA") %>% 
  summarize(RSq=(cor(`dspan_corr_pre-degree`, 
                       `grade_terp_1st year`))^2)

# Digit Span pre-degree vs. Interpreting Grades 2nd year
( fig7b <- apt_wide %>%
  ggplot(aes(x = `dspan_corr_pre-degree`, y = `grade_terp_2nd year`)) +
  geom_smooth(method= "lm") +
  geom_point(size = 2) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  coord_cartesian(xlim = c(.51, .87)) +  
  theme_minimal() + theme_details + 
  labs(title = "b) Initial Auditory WM vs. 2nd year Interpreting Grade", 
       y = "2nd year Interpreting Grade", 
       x = "Initial Digit Span Accuracy") )

# correlation
apt_wide %>% 
  filter(`dspan_corr_pre-degree`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`dspan_corr_pre-degree`, 
                       `grade_terp_2nd year`))^2)

# linear model
lm(`grade_terp_2nd year` ~ `dspan_corr_pre-degree` +
                   self_rating, data = apt_wide) %>% summary()

# Digit Span 2nd year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_2nd year`, y = `grade_terp_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "Digit Span 2nd year vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "Digit Span pre-degree")

# correlation
apt_wide %>% 
  filter(`dspan_corr_2nd year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>%
  summarize(RSq=(cor(`dspan_corr_2nd year`, 
                       `grade_terp_2nd year`))^2)
```

##### vs Eng>BSL interpreting
```{r dspan_e2b_terp}
# Digit Span pre-degree vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_pre-degree`, y = `terp_e2b_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(.63, .81)) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "Digit Span pre-degree vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "Digit Span pre-degree")

# correlation
apt_wide %>% 
  filter(`dspan_corr_pre-degree`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`dspan_corr_pre-degree`, 
                       `terp_e2b_3rd year`))^2)

# Digit Span 2nd year vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_2nd year`, y = `terp_e2b_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(.63, .81)) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "Digit Span 2nd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "Digit Span 2nd year")

# correlation
apt_wide %>% 
  filter(`dspan_corr_2nd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`dspan_corr_2nd year`, 
                       `terp_e2b_3rd year`))^2)

# Digit Span 3rd year vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_3rd year`, y = `terp_e2b_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(.7, .86)) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "Digit Span 3rd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "Digit Span 3rd year")

# correlation
apt_wide %>% 
  filter(`dspan_corr_3rd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`dspan_corr_3rd year`, 
                       `terp_e2b_3rd year`))^2)
```

##### vs BSL>Eng interpreting
```{r dspan_b2e_terp}
# Digit Span pre-degree vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_pre-degree`, y = `terp_b2e_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(.63, .72)) +
  theme_minimal() + theme_details + 
  labs(title = "Digit Span pre-degree vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "Digit Span pre-degree")

# correlation
apt_wide %>% 
  filter(`dspan_corr_pre-degree`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`dspan_corr_pre-degree`, 
                       `terp_b2e_3rd year`))^2)

# Digit Span 2nd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_2nd year`, y = `terp_b2e_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") + 
  coord_cartesian(xlim = c(.63, .79)) +
  theme_minimal() + theme_details + 
  labs(title = "Digit Span 2nd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "Digit Span 2nd year")

# correlation
apt_wide %>% 
  filter(`dspan_corr_2nd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`dspan_corr_2nd year`, 
                       `terp_b2e_3rd year`))^2)

# Digit Span 3rd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_3rd year`, y = `terp_b2e_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title = "Digit Span 3rd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "Digit Span 3rd year")

# correlation
apt_wide %>% 
  filter(`dspan_corr_3rd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`dspan_corr_3rd year`, 
                       `terp_b2e_3rd year`))^2)
```

Combine plots for Figure 7 using patchwork:
```{r}
( fig7 <- (fig7a | fig7b) )
ggsave("plots/fig7.jpeg", plot=fig7, width = 12, height = 5, units = "in")
```

#### Summarising Task

##### vs Interpreting Grades
```{r summ_grade_terp}
# Summarising pre-degree vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `summ_pre-degree`, y = `grade_terp_2nd year`)) +
  geom_smooth(method= "lm") +
  geom_point(size = 2) +
  theme_minimal() + theme_details + 
  labs(title = "Summarising pre-degree vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "Summarising pre-degree")

# correlation
apt_wide %>% 
  filter(`summ_pre-degree`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`summ_pre-degree`, 
                       `grade_terp_2nd year`))^2)
```

##### vs Eng>BSL interpreting
```{r summ_terp_e2b}
# Summarising pre-degree vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `summ_pre-degree`, y = `terp_e2b_3rd year`)) +
  geom_smooth(method= "lm") +
  geom_point(size = 2) +
  theme_minimal() + theme_details + 
  labs(title = "Summarising pre-degree vs. English to BSL interpreting 3rd year", 
       y = "English to BSL interpreting 3rd year", x = "Summarising pre-degree")

# correlation
apt_wide %>% 
  filter(`summ_pre-degree`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`summ_pre-degree`, 
                       `terp_e2b_3rd year`))^2)
```

##### vs BSL>Eng interpreting
```{r summ_terp_b2e}
# Summarising pre-degree vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `summ_pre-degree`, y = `terp_b2e_3rd year`)) +
  geom_smooth(method= "lm") +
  geom_point(size = 2) +
  theme_minimal() + theme_details + 
  labs(title = "Summarising pre-degree vs. BSL to English interpreting 3rd year", 
       y = "BSL to English interpreting 3rd year", x = "Summarising pre-degree")

# correlation
apt_wide %>% 
  filter(`summ_pre-degree`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`summ_pre-degree`, 
                       `terp_b2e_3rd year`))^2)
```

### Interpreting: no predicted impact
Now we examine the predictor variables where we hypothesised there was unlikely to be a relationship with SLI outcomes.

#### Kirklees Sentence Reading

##### vs Interpreting Grades
```{r kirk_terp_grade}
# Kirklees Sentence Reading pre-degree vs. Interpreting Grades 1st year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_pre-degree`, y = `grade_terp_1st year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(.48, .93)) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "Kirklees Sentence Reading pre-degree vs. Interpreting Grades 1st year", 
       y = "1st year Interpreting grade", x = "Kirklees Sentence Reading pre-degree")

# correlation
apt_wide %>% 
  filter(`kirk_acc_pre-degree`!= "NA") %>% 
  filter(`grade_terp_1st year` != "NA") %>% 
  summarize(RSq=(cor(`kirk_acc_pre-degree`, 
                       `grade_terp_1st year`))^2)

# Kirklees Sentence Reading pre-degree vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_pre-degree`, y = `grade_terp_2nd year`)) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(.56, .93)) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  geom_point(size = 2) +
  theme_minimal() + theme_details + 
  labs(title = "Kirklees Sentence Reading pre-degree vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "Kirklees Sentence Reading pre-degree")

# correlation
apt_wide %>% 
  filter(`kirk_acc_pre-degree`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`kirk_acc_pre-degree`, 
                       `grade_terp_2nd year`))^2)

# Kirklees Sentence Reading 1st year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_1st year`, y = `grade_terp_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "Kirklees Sentence Reading 1st year vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "Kirklees Sentence Reading after 1 year")

# correlation
apt_wide %>% 
  filter(`kirk_acc_1st year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`kirk_acc_1st year`, 
                       `grade_terp_2nd year`))^2)

# Kirklees Sentence Reading 2nd year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_2nd year`, y = `grade_terp_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "Kirklees Sentence Reading 2nd year vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "Kirklees Sentence Reading 2nd year")

# correlation
apt_wide %>% 
  filter(`kirk_acc_2nd year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>%
  summarize(RSq=(cor(`kirk_acc_2nd year`, 
                       `grade_terp_2nd year`))^2)
```

##### vs Eng>BSL interpreting
```{r kirk_e2b_terp}
# Kirklees pre-degree vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_pre-degree`, y = `terp_e2b_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(.56, .93)) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "Kirklees pre-degree vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "Kirklees pre-degree")

# correlation
apt_wide %>% 
  filter(`kirk_acc_pre-degree`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`kirk_acc_pre-degree`, 
                       `terp_e2b_3rd year`))^2)

# Kirklees 2nd year vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_2nd year`, y = `terp_e2b_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") + 
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "Kirklees 2nd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "Kirklees 2nd year")

# correlation
apt_wide %>% 
  filter(`kirk_acc_2nd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`kirk_acc_2nd year`, 
                       `terp_e2b_3rd year`))^2)
```

##### vs BSL>Eng interpreting
```{r kirk_b2e_terp}
# Kirklees pre-degree vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_pre-degree`, y = `terp_b2e_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(.56, .93)) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "Kirklees pre-degree vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "Kirklees pre-degree")

# correlation
apt_wide %>% 
  filter(`kirk_acc_pre-degree`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`kirk_acc_pre-degree`, 
                       `terp_b2e_3rd year`))^2)

# Kirklees 2nd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_2nd year`, y = `terp_b2e_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "Kirklees 2nd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "Kirklees 2nd year")

# correlation
apt_wide %>% 
  filter(`kirk_acc_2nd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`kirk_acc_2nd year`, 
                       `terp_b2e_3rd year`))^2)
```

#### KBIT-2 Matrices 

##### vs Interpreting Grades
```{r kbit_grade_terp}
# KBIT-2 Matrices pre-degree vs. Interpreting Grades 1st year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_pre-degree`, y = `grade_terp_1st year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(.82, .95)) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "KBIT-2 Matrices pre-degree vs. Interpreting Grades 1st year", 
       y = "1st year Interpreting grade", x = "KBIT-2 Matrices pre-degree")

# correlation
apt_wide %>% 
  filter(`kbit_acc_pre-degree`!= "NA") %>% 
  filter(`grade_terp_1st year` != "NA") %>% 
  summarize(RSq=(cor(`kbit_acc_pre-degree`, 
                       `grade_terp_1st year`))^2)

# KBIT-2 Matrices pre-degree vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_pre-degree`, y = `grade_terp_2nd year`)) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  geom_point(size = 2) +
  theme_minimal() + theme_details + 
  labs(title = "KBIT-2 Matrices pre-degree vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "KBIT-2 Matrices pre-degree")

# correlation
apt_wide %>% 
  filter(`kbit_acc_pre-degree`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`kbit_acc_pre-degree`, 
                       `grade_terp_2nd year`))^2)

# KBIT-2 Matrices 1st year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_1st year`, y = `grade_terp_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "KBIT-2 Matrices 1st year vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "KBIT-2 Matrices 1st year")

# correlation
apt_wide %>% 
  filter(`kbit_acc_1st year` != "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`kbit_acc_1st year`, 
                       `grade_terp_2nd year`))^2)

# KBIT-2 Matrices 2nd year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_2nd year`, y = `grade_terp_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "KBIT-2 Matrices 2nd year vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "KBIT-2 Matrices 2nd year")

# correlation
apt_wide %>% 
  filter(`kbit_acc_2nd year` != "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`kbit_acc_2nd year`, 
                       `grade_terp_2nd year`))^2)
```

##### vs Eng>BSL interpreting
```{r kbit_e2b_terp}
# KBIT-2 Matrices pre-degree vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_pre-degree`, y = `terp_e2b_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(.84, 1)) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "KBIT-2 Matrices pre-degree vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "KBIT-2 Matrices pre-degree")

# correlation
apt_wide %>% 
  filter(`kbit_acc_pre-degree`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`kbit_acc_pre-degree`, 
                       `terp_e2b_3rd year`))^2)

# KBIT-2 Matrices 2nd year vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_2nd year`, y = `terp_e2b_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "KBIT-2 Matrices 2nd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "KBIT-2 Matrices 2nd year")

# correlation
apt_wide %>% 
  filter(`kbit_acc_2nd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`kbit_acc_2nd year`, 
                       `terp_e2b_3rd year`))^2)
```

##### vs BSL>Eng interpreting
```{r kbit_b2e_terp}
# KBIT-2 Matrices pre-degree vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_pre-degree`, y = `terp_b2e_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(.84, 1)) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "KBIT-2 Matrices pre-degree vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "KBIT-2 Matrices pre-degree")

# correlation
apt_wide %>% 
  filter(`kbit_acc_pre-degree`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`kbit_acc_pre-degree`, 
                       `terp_b2e_3rd year`))^2)

# KBIT-2 Matrices 2nd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_2nd year`, y = `terp_b2e_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() + theme_details + 
  labs(title = "KBIT-2 Matrices 2nd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "KBIT-2 Matrices 2nd year")

# correlation
apt_wide %>% 
  filter(`kbit_acc_2nd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`kbit_acc_2nd year`, 
                       `terp_b2e_3rd year`))^2)
```

#### 2D Mental Rotation
##### vs Interpreting Grades
```{r mr2d_terp}
# 2D Mental Rotation pre-degree vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_pre-degree`, y = `grade_terp_2nd year`)) +
  geom_smooth(method= "lm") +
  geom_point(size = 2) +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  theme_minimal() + theme_details + 
  labs(title = "2D Mental Rotation pre-degree vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "2D Mental Rotation pre-degree")

# correlation
apt_wide %>% 
  filter(`mr2d_sats_pre-degree`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`mr2d_sats_pre-degree`, 
                       `grade_terp_2nd year`))^2)

# 2D Mental Rotation 1st year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_2nd year`, y = `grade_terp_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(-1.5, 1.5)) +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  theme_minimal() + theme_details + 
  labs(title = "2D Mental Rotation 2nd year vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "2D Mental Rotation 1st year")

# correlation
apt_wide %>% 
  filter(`mr2d_sats_2nd year` != "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`mr2d_sats_2nd year`, 
                       `grade_terp_2nd year`))^2)

lm(`grade_terp_2nd year` ~ `mr2d_sats_2nd year` +
                   self_rating, data = apt_wide) %>% summary()

# 2D Mental Rotation 2nd year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_3rd year`, y = `grade_terp_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(-.5, 1)) +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  theme_minimal() + theme_details + 
  labs(title = "2D Mental Rotation 3rd year vs. Interpreting Grades 2nd year", 
       y = "3rd year Interpreting grade", x = "2D Mental Rotation 2nd year")

# correlation
apt_wide %>% 
  filter(`mr2d_sats_3rd year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>%   
  summarize(RSq=(cor(`mr2d_sats_3rd year`, 
                       `grade_terp_2nd year`))^2)

# linear model
lm(`grade_terp_2nd year` ~ `mr2d_sats_3rd year` +
                   self_rating, data = apt_wide) %>% summary()
```

##### vs Eng>BSL interpreting
```{r mr2d_e2b_terp}
# 2D Mental Rotation 2nd year vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_2nd year`, y = `terp_e2b_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  theme_minimal() + theme_details + 
  labs(title = "2D Mental Rotation 2nd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "2D Mental Rotation 2nd year")

# correlation
apt_wide %>% 
  filter(`mr2d_sats_2nd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`mr2d_sats_2nd year`, 
                       `terp_e2b_3rd year`))^2)

# linear model
lm(`terp_e2b_3rd year` ~ `mr2d_sats_2nd year` +
                   self_rating, data = apt_wide) %>% summary()

# 2D Mental Rotation 3rd year vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_3rd year`, y = `terp_e2b_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  theme_minimal() + theme_details + 
  labs(title = "2D Mental Rotation 3rd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "2D Mental Rotation 3rd year")

# correlation
apt_wide %>% 
  filter(`mr2d_sats_3rd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`mr2d_sats_3rd year`, 
                       `terp_e2b_3rd year`))^2)

# linear model
lm(`terp_e2b_3rd year` ~ `mr2d_sats_3rd year` +
                   self_rating, data = apt_wide) %>% summary()
```

##### vs BSL>Eng interpreting
```{r mr2d_b2e_terp}
# 2D Mental Rotation 2nd year vs. BSL to Eng interpreting 3rd year
( fig8a <- apt_wide %>%
  ggplot(aes(x = `mr2d_sats_2nd year`, y = `terp_b2e_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  coord_cartesian(xlim = c(-1.3, 1.3)) +
  theme_minimal() + theme_details + 
  labs(title = "a) 2nd year 2D Mental Rotation vs. 3rd year BSL>Eng interp.",
       y = "3rd year BSL>Eng interpreting", x = "2nd year 2D Mental Rotation") )

# correlation
apt_wide %>% 
  filter(`mr2d_sats_2nd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`mr2d_sats_2nd year`, 
                       `terp_b2e_3rd year`))^2)

# linear model
lm(`terp_b2e_3rd year` ~ `mr2d_sats_2nd year` +
                   self_rating, data = apt_wide) %>% summary()

# 2D Mental Rotation 3rd year vs. BSL to Eng interpreting 3rd year
( fig8b <- apt_wide %>%
  ggplot(aes(x = `mr2d_sats_3rd year`, y = `terp_b2e_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  coord_cartesian(xlim = c(-0.5, 1.4)) +
  theme_minimal() + theme_details + 
  labs(title = "b) 3rd yr 2D Mental Rotation vs. 3rd yr BSL>Eng interp.",
       y = "3rd year BSL>Eng interpreting", x = "3rd year 2D Mental Rotation") )

# correlation
apt_wide %>% 
  filter(`mr2d_sats_3rd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`mr2d_sats_3rd year`, 
                       `terp_b2e_3rd year`))^2)

# linear model
lm(`terp_b2e_3rd year` ~ `mr2d_sats_3rd year` +
                   self_rating, data = apt_wide) %>% summary()
```

#### 3D Mental Rotation 
##### vs Interpreting Grades
```{r mr3d_grade_terp}
# 3D Mental Rotation pre-degree vs. Interpreting Grades 1st year
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_pre-degree`, y = `grade_terp_1st year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(-2, 1.5)) +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  theme_minimal() + theme_details + 
  labs(title = "3D Mental Rotation pre-degree vs. Interpreting Grades 1st year", 
       y = "1st year Interpreting grade", x = "3D Mental Rotation pre-degree")

# correlation
apt_wide %>% 
  filter(`mr3d_sats_pre-degree`!= "NA") %>% 
  filter(`grade_terp_1st year` != "NA") %>% 
  summarize(RSq=(cor(`mr3d_sats_pre-degree`, 
                       `grade_terp_1st year`))^2)

# 3D Mental Rotation pre-degree vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_pre-degree`, y = `grade_terp_2nd year`)) +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  geom_point(size = 2) +
  theme_minimal() + theme_details + 
  labs(title= "3D Mental Rotation pre-degree vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "3D Mental Rotation pre-degree") 

# correlation
apt_wide %>% 
  filter(`mr3d_sats_pre-degree`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`mr3d_sats_pre-degree`, 
                       `grade_terp_2nd year`))^2)

# 3D Mental Rotation 2nd year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_2nd year`, y = `grade_terp_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  theme_minimal() + theme_details + 
  labs(title= "3D Mental Rotation 2nd year vs. Interpreting Grades 2nd year",
       y = "2nd year Interpreting grade", x = "3D Mental Rotation 2nd year") 

# correlation
apt_wide %>% 
  filter(`mr3d_sats_2nd year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>%   
  summarize(RSq=(cor(`mr3d_sats_2nd year`, 
                       `grade_terp_2nd year`))^2)

# 3D Mental Rotation 3rd year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_3rd year`, y = `grade_terp_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  theme_minimal() + theme_details + 
  labs(title= "3D Mental Rotation 3rd year vs. Interpreting Grades 2nd year",
       y = "2nd year Interpreting grade", x = "3D Mental Rotation 3rd year") 

# correlation
apt_wide %>% 
  filter(`mr3d_sats_3rd year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>%   
  summarize(RSq=(cor(`mr3d_sats_3rd year`, 
                       `grade_terp_2nd year`))^2)

# linear model
lm(`grade_terp_2nd year` ~ `mr3d_sats_3rd year` +
                   self_rating, data = apt_wide) %>% summary()
```

##### vs Eng>BSL interpreting
```{r mr3d_e2b_terp}
# 3D Mental Rotation pre-degree vs. Eng to BSL interpreting 3rd year
( fig8c <- apt_wide %>%
  ggplot(aes(x = `mr3d_sats_pre-degree`, y = `terp_e2b_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(-2.7, 1.1)) +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  theme_minimal() + theme_details + 
  labs(title = "c) Initial 3D Mental Rotation vs. 3rd yr Eng>BSL interp.",
       y = "3rd year Eng>BSL interpreting", x = "Initial 3D Mental Rotation") )

# correlation
apt_wide %>% 
  filter(`mr3d_sats_pre-degree`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`mr3d_sats_pre-degree`, 
                       `terp_e2b_3rd year`))^2)

# linear model
lm(`terp_e2b_3rd year` ~ `mr3d_sats_pre-degree` +
                   self_rating, data = apt_wide) %>% summary()

# 3D Mental Rotation 2nd year vs. Eng to BSL interpreting  3rd year
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_2nd year`, y = `terp_e2b_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(-1.2, 2.2)) +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  theme_minimal() + theme_details + 
  labs(title = "3D Mental Rotation 2nd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "3D Mental Rotation 2nd year")

# correlation
apt_wide %>% 
  filter(`mr3d_sats_2nd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`mr3d_sats_2nd year`, 
                       `terp_e2b_3rd year`))^2)

# 3D Mental Rotation 3rd year vs. Eng to BSL interpreting  3rd year
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_3rd year`, y = `terp_e2b_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  theme_minimal() + theme_details + 
  labs(title = "3D Mental Rotation 3rd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "3D Mental Rotation 3rd year")

# correlation
apt_wide %>% 
  filter(`mr3d_sats_3rd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`mr3d_sats_3rd year`, 
                       `terp_e2b_3rd year`))^2)
```

##### vs BSL>Eng interpreting
```{r mr3d_b2e_terp}
# 3D Mental Rotation pre-degree vs. BSL to Eng interpreting 3rd year
( fig8d <- apt_wide %>%
  ggplot(aes(x = `mr3d_sats_pre-degree`, y = `terp_b2e_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(-2.7, 1.2)) +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  theme_minimal() + theme_details + 
  labs(title = "d) Initial 3D Mental Rotation vs. 3rd yr BSL>Eng interp.",
       y = "3rd year BSL>Eng interpreting", x = "Initial 3D Mental Rotation") )

# correlation
apt_wide %>% 
  filter(`mr3d_sats_pre-degree`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`mr3d_sats_pre-degree`, 
                       `terp_b2e_3rd year`))^2)

# linear model
lm(`terp_b2e_3rd year` ~ `mr3d_sats_pre-degree` +
                   self_rating, data = apt_wide) %>% summary()

# 3D Mental Rotation 2nd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_2nd year`, y = `terp_b2e_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(-1.2, 2.2)) +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  theme_minimal() + theme_details + 
  labs(title = "3D Mental Rotation 2nd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "3D Mental Rotation 2nd year")

# correlation
apt_wide %>% 
  filter(`mr3d_sats_2nd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`mr3d_sats_2nd year`, 
                       `terp_b2e_3rd year`))^2)

# 3D Mental Rotation 3rd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_3rd year`, y = `terp_b2e_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .4, linetype = "dashed") +
  theme_minimal() + theme_details + 
  labs(title = "3D Mental Rotation 3rd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "3D Mental Rotation 2nd year")

# correlation
apt_wide %>% 
  filter(`mr3d_sats_3rd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(RSq=(cor(`mr3d_sats_3rd year`, 
                       `terp_b2e_3rd year`))^2)
```
Combine plots for Figure 8 using patchwork:
```{r}
( fig8 <- (fig8a | fig8b)/(fig8c | fig8d) )
ggsave("plots/Fig8.jpeg", plot=fig8, width = 12, height = 8, units = "in")
```

#### Barratt Impulsiveness Scale 

##### vs Interpreting Grades
```{r bis_terp}
# Barratt Impulsiveness Scale 2nd year vs. Interpreting Grades 2nd year
apt_wide %>%
  filter(`bis_tot_2nd year` != "na") %>% 
  filter(`grade_terp_2nd year` != "na") %>% 
  ggplot(aes(x = `bis_tot_2nd year`, y = `grade_terp_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title= "Impulsivity 2nd year vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "BIS score 2nd year")

# correlation
apt_wide %>% 
  filter(`bis_tot_2nd year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`bis_tot_2nd year`, 
                       `grade_terp_2nd year`))^2)
```

##### vs Eng>BSL interpreting
```{r bis_e2b}
# Barratt Impulsiveness Scale 2nd year vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  filter(`bis_tot_2nd year` != "na") %>% 
  filter(`terp_e2b_3rd year` != "na") %>% 
  ggplot(aes(x = `bis_tot_2nd year`, y = `terp_e2b_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title= "Impulsivity 2nd year vs. Eng to BSL interpreting 3rd year", 
       y = "2nd year Interpreting grade", x = "Impulsivity 2nd year")

# correlation
apt_wide %>% 
  filter(`bis_tot_2nd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`bis_tot_2nd year`, 
                       `terp_e2b_3rd year`))^2)
```

##### vs BSL>Eng interpreting
```{r bis_b2e}
# Barratt Impulsiveness Scale 2nd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  filter(`bis_tot_2nd year` != "na") %>% 
  filter(`terp_b2e_3rd year` != "na") %>% 
  ggplot(aes(x = `bis_tot_2nd year`, y = `terp_b2e_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title= "Impulsivity 2nd year vs. BSL to Eng interpreting 3rd year", 
       y = "2nd year Interpreting grade", x = "Impulsivity 2nd year")

# correlation
apt_wide %>% 
  filter(`bis_tot_2nd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`bis_tot_2nd year`, 
                       `terp_b2e_3rd year`))^2)
```

### Correlations among predictor variables
Here we look at the relationships among predictor variables to see if they correlate
```{r}
# Do 2D- and 3D-MR correlate in second year?
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_2nd year`, y = `mr3d_sats_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title= "2nd year 2D Mental Rotation vs. 2nd year 3D Mental Rotation", 
       y = "2nd year 2D Mental Rotation", x = "2nd year 3D Mental Rotation")

# correlation
apt_wide %>% 
  filter(`mr2d_sats_2nd year`!= "NA") %>% 
  filter(`mr3d_sats_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`mr2d_sats_2nd year`, 
                       `mr3d_sats_2nd year`))^2)

# linear model
lm(`mr2d_sats_2nd year` ~ `mr3d_sats_2nd year` +
                   self_rating, data = apt_wide) %>% summary()

# Do 2D- and 3D-MR correlate in third year?
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_3rd year`, y = `mr3d_sats_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title= "3rd year 2D Mental Rotation vs. 3rd year 3D Mental Rotation", 
       y = "3rd year 2D Mental Rotation", x = "3rd year 3D Mental Rotation")

# correlation
apt_wide %>% 
  filter(`mr2d_sats_3rd year`!= "NA") %>% 
  filter(`mr3d_sats_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`mr2d_sats_3rd year`, 
                       `mr3d_sats_3rd year`))^2)

# linear model
lm(`mr3d_sats_3rd year` ~ `mr2d_sats_3rd year` +
                   self_rating, data = apt_wide) %>% summary() 
# significantly correlate with each other

# Does initial copy-sign correlate with initial BSL self-ratings?
apt_wide %>%
  ggplot(aes(x = `copy_sign_pre-degree`, y = `grade_bsl_1st year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title= "Initial copy-sign score vs. 1st year BSL grade", 
       y = "Initial copy-sign score", x = "1st year BSL grade")

# correlation
apt_wide %>% 
  filter(`copy_sign_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(RSq=(cor(`copy_sign_pre-degree`, 
                       `grade_bsl_1st year`))^2)

# linear model
lm(`grade_bsl_1st year` ~ `copy_sign_pre-degree` +
                   self_rating, data = apt_wide) %>% summary() 
# marginally insignificant
```

### Correlations among outcome variables
Now we look at relationships among outcome variables to see if they correlate
```{r}
# Does interpreting Eng>BSL correlate with interpreting BSL>Eng?
apt_wide %>%
  ggplot(aes(x = `terp_e2b_3rd year`, y = `terp_b2e_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title= "3rd year English-to-BSL interpreting vs. 3rd year BSL-to-English interpreting", 
       y = "3rd year BSL-to-English interpreting", x = "3rd year English-to-BSL interpreting")

# correlation
apt_wide %>% 
  filter(`terp_e2b_3rd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`terp_e2b_3rd year`, 
                       `terp_b2e_3rd year`))^2)

# linear model
lm(`terp_b2e_3rd year` ~ `terp_e2b_3rd year` +
                   self_rating, data = apt_wide) %>% summary() 
# significant predictor

# Does interpreting grades correlate with interpreting Eng>BSL?
apt_wide %>%
  ggplot(aes(x = `grade_terp_2nd year`, y = `terp_e2b_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +  
  coord_cartesian(xlim = c(50, 70)) +
  theme_minimal() + theme_details + 
  labs(title= "2nd year interpreting grade vs. 3rd year English-to-BSL interpreting", 
       y = "3rd year English-to-BSL interpreting", x = "2nd year interpreting grade")

# correlation
apt_wide %>% 
  filter(`terp_e2b_3rd year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`grade_terp_2nd year`, 
                       `terp_e2b_3rd year`))^2)

# linear model
lm(`terp_e2b_3rd year` ~ `grade_terp_2nd year` +
                   self_rating, data = apt_wide) %>% summary()

# Does interpreting grades correlate with interpreting BSL>Eng?
apt_wide %>%
  ggplot(aes(x = `grade_terp_2nd year`, y = `terp_b2e_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(50, 70)) +
  theme_minimal() + theme_details + 
  labs(title= "2nd year interpreting grade vs. 3rd year BSL-to-English interpreting", 
       y = "3rd year BSL-to-English interpreting", x = "2nd year interpreting grade")

# correlation
apt_wide %>% 
  filter(`terp_b2e_3rd year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`grade_terp_2nd year`, 
                       `terp_b2e_3rd year`))^2)

# linear model
lm(`terp_b2e_3rd year` ~ `grade_terp_2nd year` +
                   self_rating, data = apt_wide) %>% summary()

# Do interpreting grades correlate with BSL grades?
apt_wide %>%
  ggplot(aes(x = `grade_terp_2nd year`, y = `grade_bsl_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title= "2nd year interpreting grade vs. 2nd year BSL grade", 
       y = "2nd year BSL grade", x = "2nd year interpreting grade")

# correlation
apt_wide %>% 
  filter(`grade_bsl_2nd year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`grade_bsl_2nd year`, 
                       `grade_terp_2nd year`))^2)

# linear model
lm(`grade_bsl_2nd year` ~ `grade_terp_2nd year` +
                   self_rating, data = apt_wide) %>% summary() 
# significantly correlate

# Do 1st year BSL grades correlate with 2nd year interpreting grades?
apt_wide %>%
  ggplot(aes(x = `grade_bsl_1st year`, y = `grade_terp_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(56, 79)) +
  theme_minimal() + theme_details + 
  labs(title= "2nd year interpreting grade vs. 1st year BSL grade", 
       y = "2nd year interpreting grade", x = "1st year BSL grade")

# correlation
apt_wide %>% 
  filter(`grade_bsl_1st year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`grade_bsl_1st year`, 
                       `grade_terp_2nd year`))^2)

# linear model
lm(`grade_terp_2nd year` ~ `grade_bsl_1st year` +
                   self_rating, data = apt_wide) %>% summary() 
# significantly correlate

# Does initial copy-sign correlate with 1st-year BSL grades?
apt_wide %>%
  ggplot(aes(x = `copy_sign_pre-degree`, y = `grade_bsl_1st year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  theme_minimal() + theme_details + 
  labs(title = "Initial copy-sign score vs. 1st year BSL grade", 
       y = "1st year BSL grade", x = "Initial copy-sign score")

# correlation
apt_wide %>% 
  filter(`copy_sign_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(RSq=(cor(`copy_sign_pre-degree`, 
                       `grade_bsl_1st year`))^2)

# linear model
lm(`grade_bsl_1st year` ~ `copy_sign_pre-degree` +
                   self_rating, data = apt_wide) %>% summary() 
# interestingly, no relationship

# Does initial copy-sign correlate with 2nd-year BSL grades?
apt_wide %>%
  ggplot(aes(x = `copy_sign_pre-degree`, y = `grade_bsl_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") + 
  theme_minimal() + theme_details + 
  labs(title = "Initial copy-sign score vs. 2nd year BSL grade", 
       y = "2nd year BSL grade", x = "Initial copy-sign score")

# correlation
apt_wide %>% 
  filter(`copy_sign_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`copy_sign_pre-degree`, 
                       `grade_bsl_2nd year`))^2)

# linear model
lm(`grade_bsl_2nd year` ~ `copy_sign_pre-degree` +
                   self_rating, data = apt_wide) %>% summary()
# no relationship

# Does initial copy-sign correlate with later terp grades?
apt_wide %>%
  ggplot(aes(x = `copy_sign_pre-degree`, y = `grade_terp_2nd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm")  +
  theme_minimal() + theme_details + 
  labs(title = "Initial copy-sign score vs. 2nd year interpreting grade", 
       y = "2nd year interpreting grade", x = "Initial copy-sign score")

# correlation
apt_wide %>% 
  filter(`copy_sign_pre-degree`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(RSq=(cor(`copy_sign_pre-degree`, 
                       `grade_terp_2nd year`))^2)

# linear model
lm(`grade_terp_2nd year` ~ `copy_sign_pre-degree` +
                   self_rating, data = apt_wide) %>% summary() 
# interestingly yes (marginal)

# does initial copy-sign correlate with 3rd year BSL-SRT?
apt_wide %>%
  ggplot(aes(x = `copy_sign_pre-degree`, y = `bsl_srt_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(70, 90)) +
  theme_minimal() + theme_details + 
  labs(title = "Initial copy-sign score vs. 3rd year BSL-SRT score", 
       y = "3rd year BSL-SRT score", x = "Initial copy-sign score")

# correlation
apt_wide %>% 
  filter(`copy_sign_pre-degree`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`copy_sign_pre-degree`, 
                       `bsl_srt_3rd year`))^2)

# linear model
lm(`bsl_srt_3rd year` ~ `copy_sign_pre-degree` +
                   self_rating, data = apt_wide) %>% summary() 

# do 1st year BSL grades correlate with 3rd year BSL-SRT?
apt_wide %>%
  ggplot(aes(x = `grade_bsl_1st year`, y = `bsl_srt_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(56, 78)) +
  theme_minimal() + theme_details + 
  labs(title = "1st year BSL grade vs. 3rd year BSL-SRT score", 
       y = "3rd year BSL-SRT score", x = "1st year BSL grade")

# correlation
apt_wide %>% 
  filter(`grade_bsl_1st year`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`grade_bsl_1st year`, 
                       `bsl_srt_3rd year`))^2)

# linear model
lm(`bsl_srt_3rd year` ~ `grade_bsl_1st year` +
                   self_rating, data = apt_wide) %>% summary() # significant predictor 

# do 2nd-year BSL grades correlate with 3rd year BSL-SRT?
apt_wide %>%
  ggplot(aes(x = `grade_bsl_2nd year`, y = `bsl_srt_3rd year`)) +
  geom_point(size = 2) +
  geom_smooth(method= "lm") +
  coord_cartesian(xlim = c(50, 71)) +
  theme_minimal() + theme_details + 
  labs(title = "2nd year BSL grade vs. 3rd year BSL-SRT score", 
       y = "3rd year BSL-SRT score", x = "2nd year BSL grade")

# correlation
apt_wide %>% 
  filter(`grade_bsl_2nd year`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>% 
  summarize(RSq=(cor(`grade_bsl_2nd year`, 
                       `bsl_srt_3rd year`))^2)

# linear model
lm(`bsl_srt_3rd year` ~ `grade_bsl_2nd year` +
                   self_rating, data = apt_wide) %>% summary() 
# marginally insignificant
```


#################################################################

# Models
The below combined models are not reported in the manuscript because they are being fit on too few observations

## BSL Grades
What best predicts BSL grades?
```{r bsl-grade-models}
# wide version - pre-degree
lm(`grade_bsl_2nd year` ~ `nback_comb_pre-degree` +
     `mr3d_sats_pre-degree` + 
     `corsi_corr_pre-degree` +
     `kirk_acc_pre-degree` + 
     #`mlat_acc_pre-degree` +
     self_rating +
     #`copy_sign_pre-degree`
     `grade_bsl_1st year`,
   data = apt_wide) %>% summary()

# final assessments in 3rd year
lm(`grade_bsl_2nd year` ~ `nback_comb_3rd year` + 
     `mr3d_sats_3rd year` + 
     `mr2d_sats_3rd year` +
     `corsi_corr_3rd year` +
     `dspan_corr_3rd year` +
     self_rating,
   data = apt_wide) %>% summary() 
```

## BSL-SRT
```{r bsl-srt-models}
lm(bsl_srt ~ nback_comb + 
     mr3d_sats +       
     corsi_corr +
     self_rating,
   #kirk_acc +
   #kbit_acc + 
   #dspan_corr,
   data = apt) %>% summary()

# wide version - pre-degree
lm(`bsl_srt_3rd year` ~ 
                                  `mr3d_sats_pre-degree` + 
                                  `corsi_corr_pre-degree` +
                                  `kirk_acc_pre-degree` +
                                   self_rating, 
                                   data = apt_wide) %>% summary()

# final assessments in 3rd year
lm(`bsl_srt_3rd year` ~ `nback_comb_3rd year` + 
                                  `mr3d_sats_3rd year` + 
                                  `mr2d_sats_3rd year` +
                                  `corsi_corr_3rd year` +
                                   self_rating,
                                  #`dspan_corr_3rd year`,
                                  data = apt_wide) %>% summary()
```

## Interpreting Grades
```{r terp-grade-models}
lm(grade_terp ~ nback_spat + 
     mr3d_sats + 
     corsi_corr +
     kirk_acc + 
     dspan_corr +
     self_rating,
   data = apt) %>% summary()

# wide version - pre-degree
lm(`grade_terp_2nd year` ~ `nback_comb_pre-degree` +
     `mr3d_sats_pre-degree` + 
     `corsi_corr_pre-degree` +
     `kirk_acc_pre-degree` + 
     `dspan_corr_pre-degree`,
   data = apt_wide) %>% summary()

# final assessments in 3rd year
lm(`grade_terp_2nd year` ~ `nback_comb_3rd year` + 
     `mr3d_sats_3rd year` +
     `mr2d_sats_3rd year` +
     `corsi_corr_3rd year` +
     `dspan_corr_3rd year` +
     self_rating,
   data = apt_wide) %>% summary()
```

## BSL>Eng interpreting
```{r terp-b2e-models}
lm(terp_b2e ~ nback_spat +
     mr3d_sats + 
     corsi_corr +
     dspan_corr +
     self_rating,  
   data = apt) %>% summary()

# wide version - pre-degree
lm(`terp_b2e_3rd year` ~ `nback_comb_pre-degree` + 
     `mr3d_sats_pre-degree` + 
     `corsi_corr_pre-degree` +
     `dspan_corr_pre-degree`+
     self_rating,
     data = apt_wide) %>% summary()

lm(`terp_b2e_3rd year` ~ `mr3d_sats_pre-degree` +
     self_rating, 
   data = apt_wide) %>% summary()

# final assessments in 3rd year
lm(`terp_b2e_3rd year` ~ `nback_comb_3rd year` +
     `mr3d_sats_3rd year` + 
     `mr2d_sats_3rd year` +
     `corsi_corr_3rd year` +
     `dspan_corr_3rd year` +
     self_rating,
     data = apt_wide) %>% summary()
```

## Eng>BSL interpreting
```{r terp-e2b-models}
lm(terp_e2b ~ nback_spat +
     mr3d_sats + 
     corsi_corr +
     dspan_corr +
     self_rating,
   data = apt) %>% summary()

# wide version - pre-degree
lm(`terp_e2b_3rd year` ~ `nback_comb_pre-degree` + 
     `mr3d_sats_pre-degree` + 
     `corsi_corr_pre-degree` +
     `dspan_corr_pre-degree` +
     self_rating,
   data = apt_wide) %>% summary()

lm(`terp_e2b_3rd year` ~ `mr3d_sats_pre-degree` +
     self_rating,
   data = apt_wide) %>% summary()

# final assessments in 3rd year
lm(`terp_e2b_3rd year` ~ `nback_comb_3rd year` +
     `mr3d_sats_3rd year` + 
     `mr2d_sats_3rd year` +
     `corsi_corr_3rd year` +
     `dspan_corr_3rd year` +
     self_rating,
   data = apt_wide) %>% summary()
```
This concludes the BSL/SLI predictors analysis.