---
title: "Sign Language Interpreter Aptitude"
subtitle: "03 - Signing/Interpreting Predictors Analysis"
author:
  - name: "Freya Watkins"
    affiliation: "University of Birmingham"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    number_sections: false
    theme: flatly
    highlight: haddock
---
# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, 
                      echo = TRUE, cache = TRUE) 
```

## Load packages
```{r load_packages, message = FALSE, warning = FALSE}
library(here) # file organisation & folder location
library(tidyverse) # data wrangling & plotting
#library(plotrix) # for calculating standard error
library(scales) # scales on plots
library(lme4) # for linear mixed models
library(afex) # for linear mixed models
library(psych) # for factor analysis
```

### R / package versions used
```{r r_package_versions, message = FALSE, warning = FALSE}
R.Version() 
packageVersion('here')
packageVersion('tidyverse')
#packageVersion('plotrix') 
packageVersion('scales') 
packageVersion('lme4') 
packageVersion('afex')
packageVersion('psych')
```

## Read pre-wrangled data 
(see `00-wrangling-setup.Rmd` script)
```{r read_in_data}
here::here()
apt <- readRDS(here("data", "apt-data.rds"))
apt <- as_tibble(apt)
head(apt)
```

Filter out participants who did not progress beyond interview
```{r}
apt <- apt %>% filter(status != "rejected")
```

Convert data from long format to wide format
```{r}
apt_wide <- apt %>% 
  select(-comments) %>% 
  tidyr::pivot_wider(names_from = session,
                     values_from = c(nback_lett:grade_terp))
```

## Plots/correlations

### Predicted impact on BSL

#### Corsi Blocks

###### vs BSL Grades
```{r corsi_bsl_grades}
# Initial visuospatial skill vs. 1st year BSL grades
apt_wide %>%
  ggplot(aes(x = `corsi_corr_pre-degree`, y = `grade_bsl_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Initial visuospatial skill vs. 1st year BSL grades", 
       y = "1st year BSL grade", 
       x = "Initial Corsi Blocks score")

apt_wide %>% 
  filter(`corsi_corr_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(AccCOR=cor(`corsi_corr_pre-degree`, 
                       `grade_bsl_1st year`))

# Initial visuospatial skill vs. 2nd year BSL grades
apt_wide %>%
  ggplot(aes(x = `corsi_corr_pre-degree`, y = `grade_bsl_2nd year`)) +
  geom_smooth(method= "lm") +
  geom_point() +
  theme_minimal() +
  labs(title = "Initial visuospatial skill vs. 2nd year BSL grades", 
       y = "2nd year BSL grade", 
       x = "Initial Corsi Blocks score")

apt_wide %>% 
  filter(`corsi_corr_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`corsi_corr_pre-degree`, 
                       `grade_bsl_2nd year`))

# 1st year visuospatial skill vs. 1st year BSL grades
apt_wide %>%
  ggplot(aes(x = `corsi_corr_1st year`, y = `grade_bsl_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "1st year visuospatial skill vs. 1st year BSL grades", 
       y = "1st year BSL grade", 
       x = "1st year Corsi Blocks score ")

apt_wide %>% 
  filter(`corsi_corr_1st year`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(AccCOR=cor(`corsi_corr_1st year`, 
                       `grade_bsl_1st year`))

# 1st year visuospatial skill vs. 2nd year BSL grades
apt_wide %>%
  ggplot(aes(x = `corsi_corr_1st year`, y = `grade_bsl_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "1st year visuospatial skill vs. 2nd year BSL grades", 
       y = "1st year BSL grade", 
       x = "2nd year Corsi Blocks score ")

apt_wide %>% 
  filter(`corsi_corr_1st year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`corsi_corr_1st year`, 
                       `grade_bsl_2nd year`))

# 2nd year visuospatial skill vs. 2nd year BSL grades
apt_wide %>%
  ggplot(aes(x = `corsi_corr_2nd year`, y = `grade_bsl_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "2nd year visuospatial skill vs. 2nd year BSL grades", 
       y = "2nd year BSL grade", 
       x = "2nd year Corsi Blocks score ")

apt_wide %>% 
  filter(`corsi_corr_2nd year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>%
  summarize(AccCOR=cor(`corsi_corr_2nd year`, 
                       `grade_bsl_2nd year`))
```

###### vs BSL-SRT
Does Corsi Blocks performance relate to BSL Sentence Reproduction Task?
``` {r corsi_srt}
# Initial Corsi Blocks score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `corsi_corr_pre-degree`, y = `bsl_srt_3rd year`)) +
  geom_smooth(method= "lm") +
  geom_point() +
  theme_minimal() +
  labs(title = "Initial Corsi Blocks score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", 
       x = "Initial Corsi Blocks score")

apt_wide %>% 
  filter(`corsi_corr_pre-degree`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>% 
  summarize(AccCOR=cor(`corsi_corr_pre-degree`, 
                       `bsl_srt_3rd year`))

# 2nd year Corsi Blocks score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `corsi_corr_2nd year`, y = `bsl_srt_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "2nd year Corsi Blocks score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", 
       x = "2nd year Corsi Blocks score")

apt_wide %>% 
  filter(`corsi_corr_2nd year`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`corsi_corr_2nd year`, 
                       `bsl_srt_3rd year`))

# 3rd year Corsi Blocks score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `corsi_corr_3rd year`, y = `bsl_srt_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "3rd year Corsi Blocks score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", 
       x = "3rd year Corsi Blocks score")

apt_wide %>% 
  filter(`corsi_corr_3rd year`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`corsi_corr_3rd year`, 
                       `bsl_srt_3rd year`))
```


#### 2D Mental Rotation

###### vs BSL Grades
Does 2D Mental Rotation performance relate to BSL grades?
``` {r mr2d_bsl_grades}
# Initial 2D Mental Rotation score vs. 1st year BSL grades
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_pre-degree`, y = `grade_bsl_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .3) +
  theme_minimal() +
  labs(title = "Initial 2D Mental Rotation score vs. 1st year BSL grades", 
       y = "1st year BSL grade", 
       x = "Initial 2D Mental Rotation score")

apt_wide %>% 
  filter(`mr2d_sats_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(AccCOR=cor(`mr2d_sats_pre-degree`, 
                       `grade_bsl_1st year`))

# Initial 2D Mental Rotation score vs. 2nd year BSL grades
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_pre-degree`, y = `grade_bsl_2nd year`)) +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .3) +
  geom_point() +
  theme_minimal() +
  labs(title = "Initial 2D Mental Rotation score vs. 2nd year BSL grades", 
       y = "2nd year BSL grade", 
       x = "Initial 2D Mental Rotation score")

apt_wide %>% 
  filter(`mr2d_sats_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`mr2d_sats_pre-degree`, 
                       `grade_bsl_2nd year`))

# 1st year 2D Mental Rotation score vs. 1st year BSL grades
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_1st year`, y = `grade_bsl_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .3) +
  theme_minimal() +
  labs(title = "1st year 2D Mental Rotation score vs. 1st year BSL grades", 
       y = "1st year BSL grade", 
       x = "1st year 2D Mental Rotation score")

apt_wide %>% 
  filter(`mr2d_sats_1st year`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(AccCOR=cor(`mr2d_sats_1st year`, 
                       `grade_bsl_1st year`))

# 1st year 2D Mental Rotation score vs. 2nd year BSL grades
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_1st year`, y = `grade_bsl_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .3) +
  theme_minimal() +
  labs(title = "1st year 2D Mental Rotation score vs. 2nd year BSL grades", 
       y = "1st year BSL grade", 
       x = "2nd year 2D Mental Rotation score")

apt_wide %>% 
  filter(`mr2d_sats_1st year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`mr2d_sats_1st year`, 
                       `grade_bsl_2nd year`))

# 2nd year 2D Mental Rotation score vs. 2nd year BSL grades
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_2nd year`, y = `grade_bsl_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  geom_vline(xintercept = 0, alpha = .3) +
  theme_minimal() +
  labs(title = "2nd year 2D Mental Rotation score vs. 2nd year BSL grades", 
       y = "2nd year BSL grade", 
       x = "2nd year 2D Mental Rotation score")

apt_wide %>% 
  filter(`mr2d_sats_2nd year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>%   
  summarize(AccCOR=cor(`mr2d_sats_2nd year`, 
                       `grade_bsl_2nd year`))
```

###### vs BSL-SRT
Does 2D Mental Rotation performance relate to BSL Sentence Reproduction Task?
``` {r mr2d_bsl_srt}
# Initial 2D Mental Rotation score vs. 1st year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_pre-degree`, y = `bsl_srt_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Initial 2D Mental Rotation score vs. 1st year BSL-SRT scores", 
       y = "1st year BSL-SRT score", 
       x = "Initial 2D Mental Rotation score")

apt_wide %>% 
  filter(`mr2d_sats_pre-degree`!= "NA") %>% 
  filter(`bsl_srt_1st year` != "NA") %>% 
  summarize(AccCOR=cor(`mr2d_sats_pre-degree`, 
                       `bsl_srt_1st year`))

# Initial 2D Mental Rotation score vs. 2nd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_pre-degree`, y = `bsl_srt_2nd year`)) +
  geom_smooth(method= "lm") +
  geom_point() +
  theme_minimal() +
  labs(title = "Initial 2D Mental Rotation score vs. 2nd year BSL-SRT scores", 
       y = "2nd year BSL-SRT score", 
       x = "Initial 2D Mental Rotation score")

apt_wide %>% 
  filter(`mr2d_sats_pre-degree`!= "NA") %>% 
  filter(`bsl_srt_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`mr2d_sats_pre-degree`, 
                       `bsl_srt_2nd year`))

# 1st year 2D Mental Rotation score vs. 1st year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_1st year`, y = `bsl_srt_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "1st year 2D Mental Rotation score vs. 1st year BSL-SRT scores", 
       y = "1st year BSL-SRT score", 
       x = "1st year 2D Mental Rotation score")

apt_wide %>% 
  filter(`mr2d_sats_1st year`!= "NA") %>% 
  filter(`bsl_srt_1st year` != "NA") %>% 
  summarize(AccCOR=cor(`mr2d_sats_1st year`, 
                       `bsl_srt_1st year`))

# 1st year 2D Mental Rotation score vs. 2nd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_1st year`, y = `bsl_srt_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "1st year 2D Mental Rotation score vs. 2nd year BSL-SRT scores", 
       y = "1st year BSL-SRT score", 
       x = "2nd year 2D Mental Rotation score")

apt_wide %>% 
  filter(`mr2d_sats_1st year`!= "NA") %>% 
  filter(`bsl_srt_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`mr2d_sats_1st year`, 
                       `bsl_srt_2nd year`))

# 2nd year 2D Mental Rotation score vs. 2nd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_2nd year`, y = `bsl_srt_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "2nd year 2D Mental Rotation score vs. 2nd year BSL-SRT scores", 
       y = "2nd year BSL-SRT score", 
       x = "2nd year 2D Mental Rotation score")

apt_wide %>% 
  filter(`mr2d_sats_2nd year`!= "NA") %>% 
  filter(`bsl_srt_2nd year` != "NA") %>%   
  summarize(AccCOR=cor(`mr2d_sats_2nd year`, 
                       `bsl_srt_2nd year`))

# 3rd year 2D Mental Rotation score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_3rd year`, y = `bsl_srt_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "3rd year 2D Mental Rotation score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", 
       x = "3rd year 2D Mental Rotation score")
```


#### 3D Mental Rotation 

##### vs BSL Grades
Does 3D Mental Rotation performance relate to BSL grades?
``` {r mr3d_bsl_grades}
# Initial 3D Mental Rotation score vs. 1st year BSL grades
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_pre-degree`, y = `grade_bsl_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Initial 3D Mental Rotation score vs. 1st year BSL grades", 
       y = "1st year BSL grade", 
       x = "Initial 3D Mental Rotation score")

apt_wide %>% 
  filter(`mr3d_sats_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(AccCOR=cor(`mr3d_sats_pre-degree`, 
                       `grade_bsl_1st year`))

# Initial 3D Mental Rotation score vs. 2nd year BSL grades
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_pre-degree`, y = `grade_bsl_2nd year`)) +
  geom_smooth(method= "lm") +
  geom_point() +
  theme_minimal() +
  labs(title = "Initial 3D Mental Rotation score vs. 2nd year BSL grades", 
       y = "2nd year BSL grade", 
       x = "Initial 3D Mental Rotation score")

apt_wide %>% 
  filter(`mr3d_sats_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`mr3d_sats_pre-degree`, 
                       `grade_bsl_2nd year`))

# 1st year 3D Mental Rotation score vs. 1st year BSL grades
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_1st year`, y = `grade_bsl_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "1st year 3D Mental Rotation score vs. 1st year BSL grades", 
       y = "1st year BSL grade", 
       x = "1st year 3D Mental Rotation score")

apt_wide %>% 
  filter(`mr3d_sats_1st year`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(AccCOR=cor(`mr3d_sats_1st year`, 
                       `grade_bsl_1st year`))

# 1st year 3D Mental Rotation score vs. 2nd year BSL grades
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_1st year`, y = `grade_bsl_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "1st year 3D Mental Rotation score vs. 2nd year BSL grades", 
       y = "1st year BSL grade", 
       x = "2nd year 3D Mental Rotation score")

apt_wide %>% 
  filter(`mr3d_sats_1st year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`mr3d_sats_1st year`, 
                       `grade_bsl_2nd year`))

# 2nd year 3D Mental Rotation score vs. 2nd year BSL grades
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_2nd year`, y = `grade_bsl_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "2nd year 3D Mental Rotation score vs. 2nd year BSL grades", 
       y = "2nd year BSL grade", 
       x = "2nd year 3D Mental Rotation score")

apt_wide %>% 
  filter(`mr3d_sats_2nd year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>%   
  summarize(AccCOR=cor(`mr3d_sats_2nd year`, 
                       `grade_bsl_2nd year`))

```

##### vs BSL-SRT
Does 3D Mental Rotation performance relate to BSL Sentence Reproduction Task?
``` {r mr3d_bsl_srt}
# Initial 3D Mental Rotation score vs. 1st year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_pre-degree`, y = `bsl_srt_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Initial 3D Mental Rotation score vs. 1st year BSL-SRT scores", 
       y = "1st year BSL-SRT score", 
       x = "Initial 3D Mental Rotation score")

apt_wide %>% 
  filter(`mr3d_sats_pre-degree`!= "NA") %>% 
  filter(`bsl_srt_1st year` != "NA") %>% 
  summarize(AccCOR=cor(`mr3d_sats_pre-degree`, 
                       `bsl_srt_1st year`))

# Initial 3D Mental Rotation score vs. 2nd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_pre-degree`, y = `bsl_srt_2nd year`)) +
  geom_smooth(method= "lm") +
  geom_point() +
  theme_minimal() +
  labs(title = "Initial 3D Mental Rotation score vs. 2nd year BSL-SRT scores", 
       y = "2nd year BSL-SRT score", 
       x = "Initial 3D Mental Rotation score")

apt_wide %>% 
  filter(`mr3d_sats_pre-degree`!= "NA") %>% 
  filter(`bsl_srt_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`mr3d_sats_pre-degree`, 
                       `bsl_srt_2nd year`))

# Initial 3D Mental Rotation score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_pre-degree`, y = `bsl_srt_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Initial 3D Mental Rotation score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", 
       x = "Initial 3D Mental Rotation score")

apt_wide %>% 
  filter(`mr3d_sats_pre-degree`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`mr3d_sats_pre-degree`, 
                       `bsl_srt_3rd year`))

# 1st year 3D Mental Rotation score vs. 1st year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_1st year`, y = `bsl_srt_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "1st year 3D Mental Rotation score vs. 1st year BSL-SRT scores", 
       y = "1st year BSL-SRT score", 
       x = "1st year 3D Mental Rotation score")

apt_wide %>% 
  filter(`mr3d_sats_1st year`!= "NA") %>% 
  filter(`bsl_srt_1st year` != "NA") %>% 
  summarize(AccCOR=cor(`mr3d_sats_1st year`, 
                       `bsl_srt_1st year`))

# 1st year 3D Mental Rotation score vs. 2nd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_1st year`, y = `bsl_srt_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "1st year 3D Mental Rotation score vs. 2nd year BSL-SRT scores", 
       y = "1st year BSL-SRT score", 
       x = "2nd year 3D Mental Rotation score")

apt_wide %>% 
  filter(`mr3d_sats_1st year`!= "NA") %>% 
  filter(`bsl_srt_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`mr3d_sats_1st year`, 
                       `bsl_srt_2nd year`))

# 2nd year 3D Mental Rotation score vs. 2nd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_2nd year`, y = `bsl_srt_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "2nd year 3D Mental Rotation score vs. 2nd year BSL-SRT scores", 
       y = "2nd year BSL-SRT score", 
       x = "2nd year 3D Mental Rotation score")

apt_wide %>% 
  filter(`mr3d_sats_2nd year`!= "NA") %>% 
  filter(`bsl_srt_2nd year` != "NA") %>%   
  summarize(AccCOR=cor(`mr3d_sats_2nd year`, 
                       `bsl_srt_2nd year`))

# 3rd year 3D Mental Rotation score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_3rd year`, y = `bsl_srt_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "3rd year 3D Mental Rotation score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", 
       x = "3rd year 3D Mental Rotation score")

apt_wide %>% 
  filter(`mr3d_sats_3rd year`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`mr3d_sats_3rd year`, 
                       `bsl_srt_3rd year`))
```
#### MLAT Number Learning
##### vs BSL Grades
```{r mlat_grade_bsl}
# Initial MLAT Number Learning Accuracy vs. BSL grades 1st year
apt_wide %>%
  filter(`mlat_acc_pre-degree` != "na") %>% 
  filter(`grade_bsl_1st year` != "na") %>% 
  ggplot(aes(x = `mlat_acc_pre-degree`, y = `grade_bsl_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title= "Initial MLAT Number Learning Accuracy vs. BSL grades 1st year", 
       x = "MLAT Number Learning Accuracy")

apt_wide %>% 
  filter(`mlat_acc_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(AccCOR=cor(`mlat_acc_pre-degree`, 
                       `grade_bsl_1st year`))

# Initial MLAT Number Learning Accuracy vs. BSL grades 2nd year
apt_wide %>%
  filter(`mlat_acc_pre-degree` != "na") %>% 
  filter(`grade_bsl_2nd year` != "na") %>% 
  ggplot(aes(x = `mlat_acc_pre-degree`, y = `grade_bsl_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title= "Initial MLAT Number Learning Accuracy vs. BSL grades 2nd year", 
       x = "MLAT Number Learning Accuracy")

apt_wide %>% 
  filter(`mlat_acc_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`mlat_acc_pre-degree`, 
                       `grade_bsl_2nd year`))
```

##### vs BSL-SRT
```{r mlat_bsl-srt}
# Initial MLAT Number Learning Accuracy vs. BSL-SRT 3rd year
apt_wide %>%
  filter(`mlat_acc_pre-degree` != "na") %>% 
  filter(`bsl_srt_3rd year` != "na") %>% 
  ggplot(aes(x = `mlat_acc_pre-degree`, y = `bsl_srt_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title= "Initial MLAT Number Learning Accuracy vs. BSL-SRT score 3rd year", 
       x = "MLAT Number Learning Accuracy")

apt_wide %>% 
  filter(`mlat_acc_pre-degree`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>% 
  summarize(AccCOR=cor(`mlat_acc_pre-degree`, 
                       `bsl_srt_3rd year`))
```
### No predicted impact on BSL

#### Kirklees Sentence Reading

##### vs BSL Grades
```{r kirk_acc_grade_bsl}
# Kirklees Sentence Reading pre-degree vs. BSL grades 1st year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_pre-degree`, y = `grade_bsl_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() +
  labs(title = "Kirklees Sentence Reading pre-degree vs. BSL grades 1st year", y = "1st year BSL grade", x = "Kirklees Sentence Reading pre-degree")

apt_wide %>% 
  filter(`kirk_acc_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(AccCOR=cor(`kirk_acc_pre-degree`, 
                       `grade_bsl_1st year`))

# Kirklees Sentence Reading pre-degree vs. BSL grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_pre-degree`, y = `grade_bsl_2nd year`)) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  geom_point() +
  theme_minimal() +
  labs(title = "Kirklees Sentence Reading pre-degree vs. BSL grades 2nd year", y = "2nd year BSL grade", x = "Kirklees Sentence Reading pre-degree")

apt_wide %>% 
  filter(`kirk_acc_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`kirk_acc_pre-degree`, 
                       `grade_bsl_2nd year`))

# Kirklees Sentence Reading 1st year vs. BSL grades 1st year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_1st year`, y = `grade_bsl_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() +
  labs(title = "Kirklees Sentence Reading 1st year vs. BSL grades 1st year", y = "1st year BSL grade", x = "Kirklees Sentence Reading after 1 year")

apt_wide %>% 
  filter(`kirk_acc_1st year`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(AccCOR=cor(`kirk_acc_1st year`, 
                       `grade_bsl_1st year`))

# Kirklees Sentence Reading 1st year vs. BSL grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_1st year`, y = `grade_bsl_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() +
  labs(title = "Kirklees Sentence Reading 1st year vs. BSL grades 2nd year", 
       y = "2nd year BSL grade", 
       x = "Kirklees Sentence Reading after 1 year")

apt_wide %>% 
  filter(`kirk_acc_1st year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`kirk_acc_1st year`, 
                       `grade_bsl_2nd year`))

# Kirklees Sentence Reading 2nd year vs. BSL grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_2nd year`, y = `grade_bsl_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() +
  labs(title = "Kirklees Sentence Reading 2nd year vs. BSL grades 2nd year", 
       y = "2nd year BSL grade", 
       x = "Kirklees Sentence Reading 2nd year")

apt_wide %>% 
  filter(`kirk_acc_2nd year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>%
  summarize(AccCOR=cor(`kirk_acc_2nd year`, 
                       `grade_bsl_2nd year`))
```
##### vs BSL-SRT
Does Kirklees Sentence Reading performance relate to BSL Sentence Reproduction Task?
``` {r kirk_bsl_srt}
# Initial Kirklees Sentence Reading score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `kirk_acc_pre-degree`, y = `bsl_srt_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Initial Kirklees Sentence Reading score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", 
       x = "Initial Kirklees Sentence Reading score")

apt_wide %>% 
  filter(`kirk_acc_pre-degree`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`kirk_acc_pre-degree`, 
                       `bsl_srt_3rd year`))

# 2nd year Kirklees Sentence Reading score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `kirk_acc_2nd year`, y = `bsl_srt_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "2nd year Kirklees Sentence Reading score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", 
       x = "2nd year Kirklees Sentence Reading score")

apt_wide %>% 
  filter(`kirk_acc_2nd year`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`kirk_acc_2nd year`, 
                       `bsl_srt_3rd year`))
```

#### KBIT-2 Matrices 

##### vs BSL Grades
```{r kbit_acc_grade_bsl}
# KBIT-2 Matrices pre-degree vs. BSL grades 1st year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_pre-degree`, y = `grade_bsl_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "KBIT-2 Matrices pre-degree vs. BSL grades 1st year", 
       y = "1st year BSL grade", x = " ")

apt_wide %>% 
  filter(`kbit_acc_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(AccCOR=cor(`kbit_acc_pre-degree`, 
                       `grade_bsl_1st year`))

# KBIT-2 Matrices pre-degree vs. BSL grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_pre-degree`, y = `grade_bsl_2nd year`)) +
  geom_smooth(method= "lm") +
  geom_point() +
  theme_minimal() +
  labs(title = "KBIT-2 Matrices pre-degree vs. BSL grades 2nd year", 
       y = "2nd year BSL grade", x = " ")

apt_wide %>% 
  filter(`kbit_acc_pre-degree`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`kbit_acc_pre-degree`, 
                       `grade_bsl_2nd year`))

# KBIT-2 Matrices 1st year vs. BSL grades 1st year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_1st year`, y = `grade_bsl_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "KBIT-2 Matrices 1st year vs. BSL grades 1st year", 
       y = "1st year BSL grade", x = " ")

apt_wide %>% 
  filter(`kbit_acc_1st year`!= "NA") %>% 
  filter(`grade_bsl_1st year` != "NA") %>% 
  summarize(AccCOR=cor(`kbit_acc_1st year`, 
                       `grade_bsl_1st year`))

# KBIT-2 Matrices 1st year vs. BSL grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_1st year`, y = `grade_bsl_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "KBIT-2 Matrices 1st year vs. BSL grades 2nd year", 
       y = "2nd year BSL grade", x = " ")

apt_wide %>% 
  filter(`kbit_acc_1st year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`kbit_acc_1st year`, 
                       `grade_bsl_2nd year`))

# KBIT-2 Matrices 2nd year vs. BSL grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_2nd year`, y = `grade_bsl_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "KBIT-2 Matrices 2nd year vs. BSL grades 2nd year", 
       y = "2nd year BSL grade", x = " ")

apt_wide %>% 
  filter(`kbit_acc_2nd year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>%
  summarize(AccCOR=cor(`kbit_acc_2nd year`, 
                       `grade_bsl_2nd year`))
```

##### vs BSL-SRT
Does KBIT-2 Matrices performance relate to BSL Sentence Reproduction Task?
``` {r kbit_bsl_srt}
# Initial KBIT-2 Matrices score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `kbit_acc_pre-degree`, y = `bsl_srt_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Initial KBIT-2 Matrices score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", 
       x = "Initial KBIT-2 Matrices score")

apt_wide %>% 
  filter(`kbit_acc_pre-degree`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`kbit_acc_pre-degree`, 
                       `bsl_srt_3rd year`))

# 2nd year KBIT-2 Matrices score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `kbit_acc_2nd year`, y = `bsl_srt_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "2nd year KBIT-2 Matrices score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", 
       x = "2nd year KBIT-2 Matrices score")

apt_wide %>% 
  filter(`kbit_acc_2nd year`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`kbit_acc_2nd year`, 
                       `bsl_srt_3rd year`))
```

#### Digit Span 
##### vs BSL Grades
```{r dspan_bsl}
# Digit Span pre-degree vs. BSL grades 1st year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_pre-degree`, y = `grade_bsl_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Digit Span pre-degree vs. BSL grades 1st year", y = "1st year BSL grade", x = " ")

# Digit Span pre-degree vs. BSL grades 2nd year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_pre-degree`, y = `grade_bsl_2nd year`)) +
  geom_smooth(method= "lm") +
  geom_point() +
  theme_minimal() +
  labs(title = "Digit Span pre-degree vs. BSL grades 2nd year", y = "2nd year BSL grade", x = " ")

# No datapoints for Digit Span @ '1 year of study'

# Digit Span 2nd year vs. BSL grades 2nd year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_2nd year`, y = `grade_bsl_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Digit Span 2nd year vs BSL grades 2nd year", y = "2nd year BSL grade", x = " ")
```

##### vs BSL-SRT
Does Digit Span score relate to BSL-SRT score?
``` {r dspan_bsl_srt}
# Initial Digit Span score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `dspan_corr_pre-degree`, y = `bsl_srt_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Initial Digit Span score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", 
       x = "Initial Digit Span score")

apt_wide %>% 
  filter(`dspan_corr_pre-degree`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`dspan_corr_pre-degree`, 
                       `bsl_srt_3rd year`))

# 2nd year Digit Span score vs. 3rd year BSL-SRT scores
apt_wide %>%
  ggplot(aes(x = `dspan_corr_2nd year`, y = `bsl_srt_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "2nd year Digit Span score vs. 3rd year BSL-SRT scores", 
       y = "3rd year BSL-SRT score", 
       x = "2nd year Digit Span score")

apt_wide %>% 
  filter(`dspan_corr_2nd year`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`dspan_corr_2nd year`, 
                       `bsl_srt_3rd year`))
```

#### Barratt Impulsiveness Scale 
##### vs BSL Grades
```{r bis_grade_bsl}
# Barratt Impulsiveness Scale 2nd year vs BSL grades 2nd year
apt_wide %>%
  filter(`bis_tot_2nd year` != "na") %>% 
  filter(`grade_bsl_2nd year` != "na") %>% 
  ggplot(aes(x = `bis_tot_2nd year`, y = `grade_bsl_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title= "Impulsivity vs. BSL grades 2nd year", 
       y = "2nd year BSL grade", x = "BIS 2nd year")

apt_wide %>% 
  filter(`bis_tot_2nd year`!= "NA") %>% 
  filter(`grade_bsl_2nd year` != "NA") %>% 
  summarize(COR=cor(`bis_tot_2nd year`, 
                       `grade_bsl_2nd year`))
```

##### vs BSL-SRT
```{r bis_bsl_srt}
# Barratt Impulsiveness Scale 2nd year vs BSL-SRT 3rd year
apt_wide %>%
  filter(`bis_tot_2nd year` != "na") %>% 
  filter(`bsl_srt_3rd year` != "na") %>% 
  ggplot(aes(x = `bis_tot_2nd year`, y = `bsl_srt_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title= "Impulsivity 2nd year vs. BSL grades 3rd year", 
       y = "3rd year BSL grade", x = "BIS Score 2nd year")

apt_wide %>% 
  filter(`bis_tot_2nd year`!= "NA") %>% 
  filter(`bsl_srt_3rd year` != "NA") %>% 
  summarize(COR=cor(`bis_tot_2nd year`, 
                       `bsl_srt_3rd year`))
```


### Predicted impact on interpreting

#### Dual N-Back 

##### vs Interpreting Grades
```{r nback_terp_grade}
# Dual N-Back pre-degree vs. Interpreting Grades 1st year
apt_wide %>%
  ggplot(aes(x = `nback_comb_pre-degree`, y = `grade_terp_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() +
  labs(title = " Dual N-Back pre-degree vs. Interpreting Grades 1st year", 
       y = "1st year Interpreting grade", x = "Dual N-Back pre-degree")

apt_wide %>% 
  filter(`nback_comb_pre-degree`!= "NA") %>% 
  filter(`grade_terp_1st year` != "NA") %>% 
  summarize(AccCOR=cor(`nback_comb_pre-degree`, 
                       `grade_terp_1st year`))

# Dual N-Back pre-degree vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `nback_comb_pre-degree`, y = `grade_terp_2nd year`)) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  geom_point() +
  theme_minimal() +
  labs(title = " Dual N-Back pre-degree vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "Dual N-Back pre-degree")

apt_wide %>% 
  filter(`nback_comb_pre-degree`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`nback_comb_pre-degree`, 
                       `grade_terp_2nd year`))

# Dual N-Back 1st year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `nback_comb_1st year`, y = `grade_terp_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() +
  labs(title = " Dual N-Back 1st year vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "Dual N-Back 1st year")

apt_wide %>% 
  filter(`nback_comb_1st year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`nback_comb_1st year`, 
                       `grade_terp_2nd year`))

# Dual N-Back 2nd year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `nback_comb_2nd year`, y = `grade_terp_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() +
  labs(title = " Dual N-Back 2nd year vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "Dual N-Back 2nd year")

apt_wide %>% 
  filter(`nback_comb_2nd year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>%   
  summarize(AccCOR=cor(`nback_comb_2nd year`, 
                       `grade_terp_2nd year`))
```

##### vs Eng>BSL interpreting
```{r nback_e2b_terp}
#  Dual N-Back pre-degree vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `nback_comb_pre-degree`, y = `terp_e2b_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() +
  labs(title = " Dual N-Back pre-degree vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "Dual N-Back pre-degree")

apt_wide %>% 
  filter(`nback_comb_pre-degree`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>% 
  summarize(AccCOR=cor(`nback_comb_pre-degree`, 
                       `terp_e2b_3rd year`))

#  Dual N-Back 2nd year vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `nback_comb_2nd year`, y = `terp_e2b_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() +
  labs(title = " Dual N-Back 2nd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "Dual N-Back 2nd year")

apt_wide %>% 
  filter(`nback_comb_2nd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`nback_comb_2nd year`, 
                       `terp_e2b_3rd year`))

#  Dual N-Back 3rd year vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `nback_comb_3rd year`, y = `terp_e2b_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() +
  labs(title = " Dual N-Back 3rd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "Dual N-Back 3rd year")

apt_wide %>% 
  filter(`nback_comb_3rd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`nback_comb_3rd year`, 
                       `terp_e2b_3rd year`))
```

##### vs BSL>Eng interpreting
```{r nback_b2e_terp}
# Dual N-Back pre-degree vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `nback_comb_pre-degree`, y = `terp_b2e_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() +
  labs(title = " Dual N-Back pre-degree vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "Dual N-Back pre-degree")

apt_wide %>% 
  filter(`nback_comb_pre-degree`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>% 
  summarize(AccCOR=cor(`nback_comb_pre-degree`, 
                       `terp_b2e_3rd year`))

# Dual N-Back 2nd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `nback_comb_2nd year`, y = `terp_b2e_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() +
  labs(title = " Dual N-Back 2nd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "Dual N-Back 2nd year")

apt_wide %>% 
  filter(`nback_comb_2nd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`nback_comb_2nd year`, 
                       `terp_b2e_3rd year`))

# Dual N-Back 3rd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `nback_comb_3rd year`, y = `terp_b2e_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() +
  labs(title = " Dual N-Back 3rd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "Dual N-Back 3rd year")

apt_wide %>% 
  filter(`nback_comb_3rd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`nback_comb_3rd year`, 
                       `terp_b2e_3rd year`))
```

#### Corsi Blocks 
##### vs Interpreting Grades 
```{r corsi_terp}
# Corsi Blocks pre-degree vs. Interpreting Grades 1st year
apt_wide %>%
  ggplot(aes(x = `corsi_corr_pre-degree`, y = `grade_terp_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Corsi Blocks pre-degree vs. Interpreting Grades 1st year", 
       y = "1st year Interpreting grade", x = "Corsi Blocks pre-degree")

# Corsi Blocks pre-degree vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `corsi_corr_pre-degree`, y = `grade_terp_2nd year`)) +
  geom_smooth(method= "lm") +
  geom_point() +
  theme_minimal() +
  labs(title = "Corsi Blocks pre-degree vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "Corsi Blocks pre-degree")

# Corsi Blocks 1st year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `corsi_corr_1st year`, y = `grade_terp_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Corsi Blocks 1st year vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "Corsi Blocks 1st year")

# Corsi Blocks 2nd year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `corsi_corr_2nd year`, y = `grade_terp_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Corsi Blocks 2nd year vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "Corsi Blocks 2nd year")
```

##### vs Eng>BSL interpreting
```{r corsi_e2b_terp}
#  Corsi Blocks pre-degree vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `corsi_corr_pre-degree`, y = `terp_e2b_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = " Corsi Blocks pre-degree vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "Corsi Blocks pre-degree")

apt_wide %>% 
  filter(`corsi_corr_pre-degree`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>% 
  summarize(AccCOR=cor(`corsi_corr_pre-degree`, 
                       `terp_e2b_3rd year`))

#  Corsi Blocks 2nd year vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `corsi_corr_2nd year`, y = `terp_e2b_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = " Corsi Blocks 2nd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "Corsi Blocks 2nd year")

apt_wide %>% 
  filter(`corsi_corr_2nd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`corsi_corr_2nd year`, 
                       `terp_e2b_3rd year`))

#  Corsi Blocks 3rd year vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `corsi_corr_3rd year`, y = `terp_e2b_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = " Corsi Blocks 3rd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "Corsi Blocks 3rd year")

apt_wide %>% 
  filter(`corsi_corr_3rd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`corsi_corr_3rd year`, 
                       `terp_e2b_3rd year`))
```

##### vs BSL>Eng interpreting
```{r corsi_b2e_terp}
#  Corsi Blocks pre-degree vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `corsi_corr_pre-degree`, y = `terp_b2e_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = " Corsi Blocks pre-degree vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "Corsi Blocks pre-degree")

apt_wide %>% 
  filter(`corsi_corr_pre-degree`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>% 
  summarize(AccCOR=cor(`corsi_corr_pre-degree`, 
                       `terp_b2e_3rd year`))

#  Corsi Blocks 2nd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `corsi_corr_2nd year`, y = `terp_b2e_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = " Corsi Blocks 2nd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "Corsi Blocks 2nd year")

apt_wide %>% 
  filter(`corsi_corr_2nd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`corsi_corr_2nd year`, 
                       `terp_b2e_3rd year`))

#  Corsi Blocks 3rd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `corsi_corr_3rd year`, y = `terp_b2e_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = " Corsi Blocks 3rd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "Corsi Blocks 3rd year")

apt_wide %>% 
  filter(`corsi_corr_3rd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`corsi_corr_3rd year`, 
                       `terp_b2e_3rd year`))
```

#### Digit Span 

##### vs Interpreting Grades
```{r dspan_grade_terp}
# Digit Span pre-degree vs. Interpreting Grades 1st year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_pre-degree`, y = `grade_terp_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() +
  labs(title = "Digit Span pre-degree vs. Interpreting Grades 1st year", 
       y = "1st year Interpreting grade", x = "Digit Span pre-degree")

apt_wide %>% 
  filter(`dspan_corr_pre-degree`!= "NA") %>% 
  filter(`grade_terp_1st year` != "NA") %>% 
  summarize(AccCOR=cor(`dspan_corr_pre-degree`, 
                       `grade_terp_1st year`))

# Digit Span pre-degree vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_pre-degree`, y = `grade_terp_2nd year`)) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  geom_point() +
  theme_minimal() +
  labs(title = "Digit Span pre-degree vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "Digit Span pre-degree")

apt_wide %>% 
  filter(`dspan_corr_pre-degree`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`dspan_corr_pre-degree`, 
                       `grade_terp_2nd year`))

# Digit Span 2nd year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_2nd year`, y = `grade_terp_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() +
  labs(title = "Digit Span 2nd year vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "Digit Span pre-degree")

apt_wide %>% 
  filter(`dspan_corr_2nd year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>%
  summarize(AccCOR=cor(`dspan_corr_2nd year`, 
                       `grade_terp_2nd year`))
```
##### vs Eng>BSL interpreting
```{r dspan_e2b_terp}
# Digit Span pre-degree vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_pre-degree`, y = `terp_e2b_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Digit Span pre-degree vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "Digit Span pre-degree")

apt_wide %>% 
  filter(`dspan_corr_pre-degree`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>% 
  summarize(AccCOR=cor(`dspan_corr_pre-degree`, 
                       `terp_e2b_3rd year`))

# Digit Span 2nd year vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_2nd year`, y = `terp_e2b_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Digit Span 2nd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "Digit Span 2nd year")

apt_wide %>% 
  filter(`dspan_corr_2nd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`dspan_corr_2nd year`, 
                       `terp_e2b_3rd year`))

# Digit Span 3rd year vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_3rd year`, y = `terp_e2b_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Digit Span 3rd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", x = "Digit Span 3rd year")

apt_wide %>% 
  filter(`dspan_corr_3rd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`dspan_corr_3rd year`, 
                       `terp_e2b_3rd year`))
```
##### vs BSL>Eng interpreting
```{r dspan_b2e_terp}
# Digit Span pre-degree vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_pre-degree`, y = `terp_b2e_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Digit Span pre-degree vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "Digit Span pre-degree")

apt_wide %>% 
  filter(`dspan_corr_pre-degree`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>% 
  summarize(AccCOR=cor(`dspan_corr_pre-degree`, 
                       `terp_b2e_3rd year`))

# Digit Span 2nd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_2nd year`, y = `terp_b2e_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Digit Span 2nd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "Digit Span 2nd year")

apt_wide %>% 
  filter(`dspan_corr_2nd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`dspan_corr_2nd year`, 
                       `terp_b2e_3rd year`))

# Digit Span 3rd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `dspan_corr_3rd year`, y = `terp_b2e_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Digit Span 3rd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", x = "Digit Span 3rd year")

apt_wide %>% 
  filter(`dspan_corr_3rd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`dspan_corr_3rd year`, 
                       `terp_b2e_3rd year`))
```

### No predicted impact on interpreting

#### Kirklees Sentence Reading

##### vs Interpreting Grades
```{r kirk_terp_grade}
# Kirklees Sentence Reading pre-degree vs. Interpreting Grades 1st year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_pre-degree`, y = `grade_terp_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() +
  labs(title = "Kirklees Sentence Reading pre-degree vs. Interpreting Grades 1st year", 
       y = "1st year Interpreting grade", x = "Kirklees Sentence Reading pre-degree")

apt_wide %>% 
  filter(`kirk_acc_pre-degree`!= "NA") %>% 
  filter(`grade_terp_1st year` != "NA") %>% 
  summarize(AccCOR=cor(`kirk_acc_pre-degree`, 
                       `grade_terp_1st year`))

# Kirklees Sentence Reading pre-degree vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_pre-degree`, y = `grade_terp_2nd year`)) +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  geom_point() +
  theme_minimal() +
  labs(title = "Kirklees Sentence Reading pre-degree vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "Kirklees Sentence Reading pre-degree")

apt_wide %>% 
  filter(`kirk_acc_pre-degree`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`kirk_acc_pre-degree`, 
                       `grade_terp_2nd year`))

# Kirklees Sentence Reading 1st year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_1st year`, y = `grade_terp_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() +
  labs(title = "Kirklees Sentence Reading 1st year vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", 
       x = "Kirklees Sentence Reading after 1 year")

apt_wide %>% 
  filter(`kirk_acc_1st year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`kirk_acc_1st year`, 
                       `grade_terp_2nd year`))

# Kirklees Sentence Reading 2nd year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_2nd year`, y = `grade_terp_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) +
  theme_minimal() +
  labs(title = "Kirklees Sentence Reading 2nd year vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = "Kirklees Sentence Reading 2nd year")

apt_wide %>% 
  filter(`kirk_acc_2nd year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>%
  summarize(AccCOR=cor(`kirk_acc_2nd year`, 
                       `grade_terp_2nd year`))
```

##### vs Eng>BSL interpreting
```{r kirk_e2b_terp}
# Kirklees pre-degree vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_pre-degree`, y = `terp_e2b_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Kirklees pre-degree vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", 
       x = "Kirklees pre-degree")

apt_wide %>% 
  filter(`kirk_acc_pre-degree`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>% 
  summarize(AccCOR=cor(`kirk_acc_pre-degree`, 
                       `terp_e2b_3rd year`))

# Kirklees 2nd year vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_2nd year`, y = `terp_e2b_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Kirklees 2nd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year",
       x = "Kirklees 2nd year")

apt_wide %>% 
  filter(`kirk_acc_2nd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`kirk_acc_2nd year`, 
                       `terp_e2b_3rd year`))
```

##### vs BSL>Eng interpreting
```{r kirk_b2e_terp}
# Kirklees pre-degree vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_pre-degree`, y = `terp_b2e_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Kirklees pre-degree vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", 
       x = "Kirklees pre-degree")

apt_wide %>% 
  filter(`kirk_acc_pre-degree`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>% 
  summarize(AccCOR=cor(`kirk_acc_pre-degree`, 
                       `terp_b2e_3rd year`))

# Kirklees 2nd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `kirk_acc_2nd year`, y = `terp_b2e_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "Kirklees 2nd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year",
       x = "Kirklees 2nd year")

apt_wide %>% 
  filter(`kirk_acc_2nd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`kirk_acc_2nd year`, 
                       `terp_b2e_3rd year`))
```

#### KBIT-2 Matrices 

##### vs Interpreting Grades
```{r kbit_grade_terp}
# KBIT-2 Matrices pre-degree vs. Interpreting Grades 1st year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_pre-degree`, y = `grade_terp_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "KBIT-2 Matrices pre-degree vs. Interpreting Grades 1st year", 
       y = "1st year Interpreting grade", x = " ")

# KBIT-2 Matrices pre-degree vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_pre-degree`, y = `grade_terp_2nd year`)) +
  geom_smooth(method= "lm") +
  geom_point() +
  theme_minimal() +
  labs(title = "KBIT-2 Matrices pre-degree vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = " ")

# KBIT-2 Matrices 1st year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_1st year`, y = `grade_terp_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "KBIT-2 Matrices 1st year vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = " ")

# KBIT-2 Matrices 2nd year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_2nd year`, y = `grade_terp_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "KBIT-2 Matrices 2nd year vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", x = " ")
```

##### vs Eng>BSL interpreting
```{r kbit_e2b_terp}
# KBIT-2 Matrices pre-degree vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_pre-degree`, y = `terp_e2b_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "KBIT-2 Matrices pre-degree vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year", 
       x = "KBIT-2 Matrices pre-degree")

apt_wide %>% 
  filter(`kbit_acc_pre-degree`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>% 
  summarize(AccCOR=cor(`kbit_acc_pre-degree`, 
                       `terp_e2b_3rd year`))

# KBIT-2 Matrices 2nd year vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_2nd year`, y = `terp_e2b_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "KBIT-2 Matrices 2nd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year",
       x = "KBIT-2 Matrices 2nd year")

apt_wide %>% 
  filter(`kbit_acc_2nd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`kbit_acc_2nd year`, 
                       `terp_e2b_3rd year`))
```

##### vs BSL>Eng interpreting
```{r kbit_b2e_terp}
# KBIT-2 Matrices pre-degree vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_pre-degree`, y = `terp_b2e_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "KBIT-2 Matrices pre-degree vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year", 
       x = "KBIT-2 Matrices pre-degree")

apt_wide %>% 
  filter(`kbit_acc_pre-degree`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>% 
  summarize(AccCOR=cor(`kbit_acc_pre-degree`, 
                       `terp_b2e_3rd year`))

# KBIT-2 Matrices 2nd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `kbit_acc_2nd year`, y = `terp_b2e_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "KBIT-2 Matrices 2nd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year",
       x = "KBIT-2 Matrices 2nd year")

apt_wide %>% 
  filter(`kbit_acc_2nd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`kbit_acc_2nd year`, 
                       `terp_b2e_3rd year`))
```

#### 2D Mental Rotation
##### vs Interpreting Grades
```{r mr2d_terp}
# 2D Mental Rotation pre-degree vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_pre-degree`, y = `grade_terp_2nd year`)) +
  geom_smooth(method= "lm") +
  geom_point() +
  theme_minimal() +
  labs(title = "2D Mental Rotation pre-degree vs. Interpreting Grades 2nd year", y = "2nd year Interpreting grade", x = "2D Mental Rotation pre-degree")

apt_wide %>% 
  filter(`mr2d_sats_pre-degree`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`mr2d_sats_pre-degree`, 
                       `grade_terp_2nd year`))

# 2D Mental Rotation 1st year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_1st year`, y = `grade_terp_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "2D Mental Rotation 1st year vs. Interpreting Grades 2nd year", y = "2nd year Interpreting grade", x = "2D Mental Rotation 1st year")

apt_wide %>% 
  filter(`mr2d_sats_1st year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`mr2d_sats_1st year`, 
                       `grade_terp_2nd year`))

# 2D Mental Rotation 2nd year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_2nd year`, y = `grade_terp_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "2D Mental Rotation 2nd year vs. Interpreting Grades 2nd year", y = "2nd year Interpreting grade", x = "2D Mental Rotation 2nd year")

apt_wide %>% 
  filter(`mr2d_sats_2nd year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>%   
  summarize(AccCOR=cor(`mr2d_sats_2nd year`, 
                       `grade_terp_2nd year`))
```
##### vs Eng>BSL interpreting
```{r mr2d_e2b_terp}
# 2D Mental Rotation 2nd year vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_2nd year`, y = `terp_e2b_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "2D Mental Rotation 2nd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year",
       x = "2D Mental Rotation 2nd year")

apt_wide %>% 
  filter(`mr2d_sats_2nd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`mr2d_sats_2nd year`, 
                       `terp_e2b_3rd year`))

# 2D Mental Rotation 3rd year vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_3rd year`, y = `terp_e2b_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "2D Mental Rotation 3rd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year",
       x = "2D Mental Rotation 3rd year")

apt_wide %>% 
  filter(`mr2d_sats_3rd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`mr2d_sats_3rd year`, 
                       `terp_e2b_3rd year`))

```

##### vs BSL>Eng interpreting
```{r mr2d_b2e_terp}
# 2D Mental Rotation 2nd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_2nd year`, y = `terp_b2e_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "2D Mental Rotation 2nd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year",
       x = "2D Mental Rotation 2nd year")

apt_wide %>% 
  filter(`mr2d_sats_2nd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`mr2d_sats_2nd year`, 
                       `terp_b2e_3rd year`))

# 2D Mental Rotation 3rd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `mr2d_sats_3rd year`, y = `terp_b2e_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "2D Mental Rotation 3rd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year",
       x = "2D Mental Rotation 2nd year")

apt_wide %>% 
  filter(`mr2d_sats_3rd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`mr2d_sats_3rd year`, 
                       `terp_b2e_3rd year`))
```

#### 3D Mental Rotation 
##### vs Interpreting Grades
```{r mr3d_grade_terp}
# 3D Mental Rotation pre-degree vs. Interpreting Grades 1st year
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_pre-degree`, y = `grade_terp_1st year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "3D Mental Rotation pre-degree vs. Interpreting Grades 1st year", 
       y = "1st year Interpreting grade", 
       x = "3D Mental Rotation pre-degree")

apt_wide %>% 
  filter(`mr3d_sats_pre-degree`!= "NA") %>% 
  filter(`grade_terp_1st year` != "NA") %>% 
  summarize(AccCOR=cor(`mr3d_sats_pre-degree`, 
                       `grade_terp_1st year`))

# 3D Mental Rotation pre-degree vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_pre-degree`, y = `grade_terp_2nd year`)) +
  geom_smooth(method= "lm") +
  geom_point() +
  theme_minimal() +
  labs(title= "3D Mental Rotation pre-degree vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", 
       x = "3D Mental Rotation pre-degree") 

apt_wide %>% 
  filter(`mr3d_sats_pre-degree`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>% 
  summarize(AccCOR=cor(`mr3d_sats_pre-degree`, 
                       `grade_terp_2nd year`))

# 3D Mental Rotation 2nd year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_2nd year`, y = `grade_terp_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title= "3D Mental Rotation 2nd year vs. Interpreting Grades 2nd year",
       y = "2nd year Interpreting grade", 
       x = "3D Mental Rotation 2nd year") 

apt_wide %>% 
  filter(`mr3d_sats_2nd year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>%   
  summarize(AccCOR=cor(`mr3d_sats_2nd year`, 
                       `grade_terp_2nd year`))

# 3D Mental Rotation 3rd year vs. Interpreting Grades 2nd year
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_3rd year`, y = `grade_terp_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title= "3D Mental Rotation 3rd year vs. Interpreting Grades 2nd year",
       y = "2nd year Interpreting grade", 
       x = "3D Mental Rotation 3rd year") 

apt_wide %>% 
  filter(`mr3d_sats_3rd year`!= "NA") %>% 
  filter(`grade_terp_2nd year` != "NA") %>%   
  summarize(AccCOR=cor(`mr3d_sats_3rd year`, 
                       `grade_terp_2nd year`))
```

##### vs Eng>BSL interpreting
```{r mr3d_e2b_terp}
# 3D Mental Rotation pre-degree vs. Eng to BSL interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_pre-degree`, y = `terp_e2b_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "3D Mental Rotation pre-degree vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year",
       x = "3D Mental Rotation pre-degree")

apt_wide %>% 
  filter(`mr3d_sats_pre-degree`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`mr3d_sats_pre-degree`, 
                       `terp_e2b_3rd year`))

# 3D Mental Rotation 2nd year vs. Eng to BSL interpreting  3rd year
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_2nd year`, y = `terp_e2b_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "3D Mental Rotation 2nd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year",
       x = "3D Mental Rotation 2nd year")

apt_wide %>% 
  filter(`mr3d_sats_2nd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`mr3d_sats_2nd year`, 
                       `terp_e2b_3rd year`))

# 3D Mental Rotation 3rd year vs. Eng to BSL interpreting  3rd year
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_3rd year`, y = `terp_e2b_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "3D Mental Rotation 3rd year vs. Eng to BSL interpreting 3rd year",
       y = "Eng to BSL interpreting 3rd year",
       x = "3D Mental Rotation 3rd year")

apt_wide %>% 
  filter(`mr3d_sats_3rd year`!= "NA") %>% 
  filter(`terp_e2b_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`mr3d_sats_3rd year`, 
                       `terp_e2b_3rd year`))

```

##### vs BSL>Eng interpreting
```{r mr3d_b2e_terp}
# 3D Mental Rotation pre-degree vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_pre-degree`, y = `terp_b2e_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "3D Mental Rotation pre-degree vs. BSL to Eng interpreting 3rd year",
       y = "BSL to BSL interpreting 3rd year",
       x = "3D Mental Rotation pre-degree")

apt_wide %>% 
  filter(`mr3d_sats_pre-degree`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`mr3d_sats_pre-degree`, 
                       `terp_b2e_3rd year`))

# 3D Mental Rotation 2nd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_2nd year`, y = `terp_b2e_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "3D Mental Rotation 2nd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year",
       x = "3D Mental Rotation 2nd year")

apt_wide %>% 
  filter(`mr3d_sats_2nd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`mr3d_sats_2nd year`, 
                       `terp_b2e_3rd year`))

# 3D Mental Rotation 3rd year vs. BSL to Eng interpreting 3rd year
apt_wide %>%
  ggplot(aes(x = `mr3d_sats_3rd year`, y = `terp_b2e_3rd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title = "3D Mental Rotation 3rd year vs. BSL to Eng interpreting 3rd year",
       y = "BSL to Eng interpreting 3rd year",
       x = "3D Mental Rotation 2nd year")

apt_wide %>% 
  filter(`mr3d_sats_3rd year`!= "NA") %>% 
  filter(`terp_b2e_3rd year` != "NA") %>%   
  summarize(AccCOR=cor(`mr3d_sats_3rd year`, 
                       `terp_b2e_3rd year`))
```

#### Barratt Impulsiveness Scale 

##### vs Interpreting Grades
```{r bis_terp}
# Barratt Impulsiveness Scale 2nd year vs. Interpreting Grades 2nd year
apt_wide %>%
  filter(`bis_tot_2nd year` != "na") %>% 
  filter(`grade_terp_2nd year` != "na") %>% 
  ggplot(aes(x = `bis_tot_2nd year`, y = `grade_terp_2nd year`)) +
  geom_point() +
  geom_smooth(method= "lm") +
  theme_minimal() +
  labs(title= "Impulsivity 2nd year vs. Interpreting Grades 2nd year", 
       y = "2nd year Interpreting grade", 
       x = "BIS score 2nd year")
```


##############################################################################

# Models

## BSL Grades
What best predicts BSL grades?
```{r bsl-grade-models}
( bsl_grade_mdl <- lm(grade_bsl ~ nback_comb + 
                                  mr3d_sats + 
                                  corsi_corr +
                                  kirk_acc, 
                                  data = apt) ) 
summary(bsl_grade_mdl)
# only fit on 10 observations

# wide version - pre-degree
( bsl_grade_mdl_2 <- lm(`grade_bsl_2nd year` ~ 
                                  `nback_comb_pre-degree` + 
                                  `mr3d_sats_pre-degree` + 
                                  `corsi_corr_pre-degree` +
                                  `kirk_acc_pre-degree` + 
                                  #`kbit_acc_pre-degree` + 
                                  `mlat_acc_pre-degree`,
                                  #`dspan_corr_pre-degree`,
                                  data = apt_wide) ) 
summary(bsl_grade_mdl_2)

# final assessments in 3rd year
( bsl_grade_mdl_3 <- lm(`grade_bsl_2nd year` ~ `nback_comb_3rd year` + 
                                  `mr3d_sats_3rd year` + 
                                  `mr2d_sats_3rd year` +
                                  `corsi_corr_3rd year` +
                                  `dspan_corr_3rd year`,
                                  data = apt_wide) ) 
summary(bsl_grade_mdl_3)
```

## BSL-SRT
```{r bsl-srt-models}
( bsl_srt_mdl <- lm(bsl_srt ~ nback_comb + 
                                  mr3d_sats + 
                                  corsi_corr,
                                  #kirk_acc +
                                  #kbit_acc + 
                                  #dspan_corr,
                                  data = apt) ) 
summary(bsl_srt_mdl)
# only being fit on 8 or 9 observations...

# wide version - pre-degree
( bsl_srt_mdl_2 <- lm(`bsl_srt_3rd year` ~ 
                                  `nback_comb_pre-degree` + 
                                  `mr3d_sats_pre-degree` + 
                                  `corsi_corr_pre-degree` +
                                  `kirk_acc_pre-degree` + 
                                  #`kbit_acc_pre-degree` +
                                  `mlat_acc_pre-degree`, 
                                  #`dspan_corr_pre-degree`,
                                  data = apt_wide) ) 
summary(bsl_srt_mdl_2)

# final assessments in 3rd year
( bsl_srt_mdl_3 <- lm(`bsl_srt_3rd year` ~ `nback_comb_3rd year` + 
                                  `mr3d_sats_3rd year` + 
                                  `mr2d_sats_3rd year` +
                                  `corsi_corr_3rd year`,
                                  #`dspan_corr_3rd year`,
                                  data = apt_wide) ) 
summary(bsl_srt_mdl_3)
```

## Interpreting Grades
```{r terp-grade-models}
( terp_grade_mdl <- lm(grade_terp ~ nback_spat + 
                                    mr3d_sats + 
                                    corsi_corr +
                                    kirk_acc + 
                                    #kbit_acc + 
                                    dspan_corr,
                                    data = apt) )
summary(terp_grade_mdl)
# but is only being fit on 10 observations.....

# wide version - pre-degree
( terp_grade_mdl_2 <- lm(`grade_terp_2nd year` ~ 
                                  `nback_comb_pre-degree` + 
                                  #`mr3d_sats_pre-degree` + 
                                  `corsi_corr_pre-degree` +
                                  `kirk_acc_pre-degree` + 
                                  #`kbit_acc_pre-degree` +
                                  #`mlat_acc_pre-degree` +
                                  `dspan_corr_pre-degree`,
                                  data = apt_wide) )
summary(terp_grade_mdl_2)

# final assessments in 3rd year
( terp_grade_mdl_3 <- lm(`grade_terp_2nd year` ~ `nback_comb_3rd year` + 
                                  `mr3d_sats_3rd year` + 
                                  `mr2d_sats_3rd year` +
                                  `corsi_corr_3rd year` +
                                  `dspan_corr_3rd year`,
                                  data = apt_wide) ) 
summary(terp_grade_mdl_3)
```

## BSL>Eng interpreting

## Eng>BSL interpreting

##############################################################################

# Factor Analysis

reduce tibble to just independent variables:
``` {r reduce_tibble}
# apt <- select(apt, -session, -group, -ppt, -copy_score, -srt_score, -town_map, -bsl_grade)
```

filter out rows with incomplete data
``` {r filter_rows}
#apt_reduced <- filter(apt, corsi_corr != "na")
#apt_reduced <- filter(apt_reduced, nback_spat != "na")
#apt_reduced <- filter(apt_reduced, kirk_ceil != "na")
```

reduce to just four tasks that were done at all 3 sessions
```{r}
#apt_reduced <- select(apt_reduced, nback_lett:kbit_acc)
```

## FA using psych package

```{r }
# fapsych <- fa(apt_reduced, nfactors=3, rotate="oblimin", scores="regression", residuals=FALSE, fm="minres")
```

## run factor analysis
``` {r}
# FA <- factanal(apt_reduced, factors=2, rotation="varimax", scores="regression")
```
